### 2020-07-29 WorkingScriptJuly29.Rmd
Counted my sample sizes

---
title: "Working Script"
output: html_notebook
---

This script is just to play around with the data while I'm still collecting it.

## Load in packages

```{r}
library(dplyr)
library(tidyr)
```

## Load in the data

```{r}
data <- read.csv("~/Desktop/MsCcHSFeedJuly29.csv")
```

## Counting sample size

```{r}
count(data[data$food == "TB" & data$para == "yes" & data$HS == "yes", ])
count(data[data$food == "TB" & data$para == "yes" & data$HS == "no", ])
count(data[data$food == "TB" & data$para == "no" & data$HS == "yes", ])
count(data[data$food == "TB" & data$para == "no" & data$HS == "no", ])
```

```{r}
count(data[data$food == "DC" & data$para == "yes" & data$HS == "yes", ])
count(data[data$food == "DC" & data$para == "yes" & data$HS == "no", ])
count(data[data$food == "DC" & data$para == "no" & data$HS == "yes", ])
count(data[data$food == "DC" & data$para == "no" & data$HS == "no", ])
```

## Check how many have survived

```{r}
data <- data[data$survived == "yes", ]
```

```{r}
count(data[data$food == "TB" & data$para == "yes" & data$HS == "yes", ])
count(data[data$food == "TB" & data$para == "yes" & data$HS == "no", ])
count(data[data$food == "TB" & data$para == "no" & data$HS == "yes", ])
count(data[data$food == "TB" & data$para == "no" & data$HS == "no", ])
```

```{r}
count(data[data$food == "DC" & data$para == "yes" & data$HS == "yes", ])
count(data[data$food == "DC" & data$para == "yes" & data$HS == "no", ])
count(data[data$food == "DC" & data$para == "no" & data$HS == "yes", ])
count(data[data$food == "DC" & data$para == "no" & data$HS == "no", ])
```

### 2020-09-01 WorkingScript.Rmd
Renamed without date, loaded in new datafile.
Updated datasheet input
Figured out how to get the total leaf area eaten for each individual.
Preliminary model.

--- 2020-07-29 WorkingScriptJuly29.Rmd
@@
 library(tidyr)
+library(ggplot2)
+library(lme4)
 ```
@@
 ```{r}
-data <- read.csv("~/Desktop/MsCcHSFeedJuly29.csv")
+data <- read.csv("~/Desktop/MsCcHSFeedAug30.csv")
 ```
@@
 ```
+
+## Load in the leaf area data
+
+```{r}
+scan <- read.csv("~/Desktop/MsCcHSFeedLeafScanAug29.csv", header = T)
+```
+
+## Write a for-loop for getting the amounts eaten
+
+0. Create output file 
+1. Combine Leaf ID and cat ID into one ID 
+2. Parse by unique  ID
+3. Subtract min measurement from max measurement
+4. Record with comb ID
+5. Separate out catID and leaf ID
+6. Create new output structure
+7. Sum for each cat ID 
+8. Combine with main dataset as a column
+
+```{r}
+#1
+scan$comb <- paste(scan$Caterpillar.ID, "_", scan$Leaf.ID)
+
+#0
+unique <- unique(scan$comb)
+consumed <- as.data.frame(unique)
+consumed$area <- 0
+
+#2-4
+for (i in 1:length(consumed$unique)){
+    subset <- filter(scan, scan$comb == consumed[i, 1])
+    value <- max(subset$Leaf.Area) - min(subset$Leaf.Area)
+    consumed[i, 2] <- value
+}
+
+#5
+consumed <- consumed %>%
+  separate(unique, c("catID", "leafID"), "_")
+
+#6
+ID <- unique(consumed$catID)
+consumedsum <- as.data.frame(ID)
+consumedsum$totalarea <- 0
+
+#7
+for (i in 1:length(consumedsum$ID)){
+  subset2 <- filter(consumed, consumed$catID == consumedsum[i, 1])
+  value2 <- sum(subset2$area)
+  consumedsum[i, 2] <- value2
+}
+
+```
+
+Step 8 proved to be more complicated, so it's listed below...
+
+```{r}
+consumedsum$ID <- as.numeric(consumedsum$ID)
+
+consumedsum <- consumedsum[consumedsum$ID != 707, ]
+consumedsum <- consumedsum[consumedsum$ID != 1816, ]
+
+consumedsum <- consumedsum[consumedsum$ID %in% data$ID, ]
+
+data <- data[data$ID %in% consumedsum$ID, ]
+
+consumedsum <- consumedsum[order(consumedsum$ID), ]
+
+data$area <- consumedsum$totalarea
+```
+
+YAY!!!
+
+Now, let's run some preliminary analyses:
+
+```{r}
+mod1 <- lmer(area ~ food + (1|bin), data = data)
+
+summary(mod1)
+```
+
+```{r}
+dataDC <- data[data$food == "DC", ]
+dataTB <- data[data$food == "TB", ]
+
+t.test(dataDC$area, dataTB$area)
+```

### 2020-09-01 WorkingScript.Rmd
imported new dataset with fate column
Added some graphs

@@
 ```{r}
-data <- read.csv("~/Desktop/MsCcHSFeedAug30.csv")
+data <- read.csv("~/Desktop/MsCcHSFeedSep1.csv")
 ```
@@
 ```{r}
-data <- data[data$survived == "yes", ]
+data <- data[data$fate != "dead" & data$fate != "quink", ]
 ```
@@
 
-consumedsum <- consumedsum[consumedsum$ID != 707, ]
-consumedsum <- consumedsum[consumedsum$ID != 1816, ]
-
 consumedsum <- consumedsum[consumedsum$ID %in% data$ID, ]
@@
 
+# Graphing
+
+Let's graph maximum mass reached:
+
+```{r}
+ggplot(data = data, aes(x = mass.max)) + 
+  geom_histogram(binwidth = 500)
+```
+
+Now, let's graph area to see if it's "normal".
+
+```{r}
+ggplot(data, aes(x = area)) + 
+  geom_histogram(binwidth = 250)
+```
+Nope, definitely bimodal
+
+```{r}
+ggplot(data, aes(x = mass.max, y = area)) + 
+  geom_point(aes(color = fate))
+```
+
 Now, let's run some preliminary analyses:
@@
 ```{r}
-mod1 <- lmer(area ~ food + (1|bin), data = data)
+mod1 <- lm(area ~ food + fate, data = data)
 

### 2020-09-03 WorkingScript.Rmd
Added a note.
Added some models after talking with Joel.

@@
 ggplot(data, aes(x = mass.max, y = area)) + 
-  geom_point(aes(color = fate))
+  geom_point(aes(color = food))
 ```
 
-Now, let's run some preliminary analyses:
+Now, let's run some preliminary analyses (this is probably whack because it's bimodal):
 
 ```{r}
-mod1 <- lm(area ~ food + fate, data = data)
+mod1 <- lm(area ~ food*para*HS + mass.max, data = data)
 
 summary(mod1)
+```
+
+```{r}
+mod2 <- lm(mass.max ~ food*para*HS, data = data)
+
+summary(mod2)
+```
+
+```{r}
+mod3 <- lm(area ~ mass.max, data = data)
+
+summary(mod3)
 ```

### 2020-09-29 WorkingScript.Rmd
Loaded in new datasets

@@
 ```{r}
-data <- read.csv("~/Desktop/MsCcHSFeedSep1.csv")
+data <- read.csv("~/Desktop/MsCcHSFeedSep15modfinal.csv")
 ```
@@
 ```{r}
-scan <- read.csv("~/Desktop/MsCcHSFeedLeafScanAug29.csv", header = T)
+scan <- read.csv("~/Desktop/MsCcHSFeedLeafScanFinal.csv", header = T)
 ```
@@
 ggplot(data, aes(x = mass.max, y = area)) + 
-  geom_point(aes(color = food))
+  geom_point(aes(color = food)) + 
+  labs(x = "Maximum mass achieved (mg)", y = "Leaf surface area consumed (cm2)", color = "Food type")
+```
+
+```{r}
+ggplot(data, aes(x = mass.max, y = area)) + 
+  geom_point(aes(color = fate))
 ```
@@
 summary(mod1)
+```
+
+```{r}
+mod1.5 <- lm(area ~ mass.max + food, data = data)
+
+summary(mod1.5)
+```
+
+```{r}
+mod1.75 <- lm(area ~ mass.max + food*para, data = data)
+
+summary(mod1.75)
 ```
@@
 ```
+
+## Adding in random effect of bin
+
+```{r}
+mod4 <- lmer(area ~ mass.max + (1|bin), data = data)
+
+summary(mod4)
+```
+
+It's a singluar fit - I could switch all of my individual bins to the same number? Would that work?
+
+Let's check the effect of group vs. individual bins
+
+```{r}
+mod5 <- lmer(area ~ mass.max + (1|bin.type), data = data)
+
+summary(mod5)
+```
+
+```{r}
+mod6 <- lmer(mass.max ~ food*para*HS + (1|bin), data = data)
+
+summary(mod6)
+```
+
+```{r}
+mod6.5 <- lmer(mass.max ~ food + para + HS + (1|bin), data = data)
+
+summary(mod6.5)
+```
+
+The above model is the only one that isn't singular!!
+
+```{r}
+mod7 <- lmer(mass.max ~ food*para*HS + (1|bin.type), data = data)
+
+summary(mod7)
+```
+
+```{r}
+mod8 <- lmer(mass.max ~ para*HS + (1|bin), data = data)
+
+summary(mod8)
+```
+
+Let's test some models with AIC
+
+```{r}
+AIC(mod1, mod1.5, mod1.75, mod3, mod4, mod5)
+```
+
+Model 1 and model 1.75 are indistinguishable - so you need food and para and their interaction to get the full picture for area
+
+```{r}
+AIC(mod2,mod6, mod6.5, mod7, mod8)
+```
+
+Mods 6 and 7 are indistinguishable - you need the random effect of bin, but bin and bin type have the same effect? You also need all the interactive terms, even though they aren't significant.
+
+```{r}
+data2 <- read.csv("~/Desktop/MsCcHSFeedSep15binmod2.csv")
+```
+
+```{r}
+consumedsum2 <- consumedsum[consumedsum$ID %in% data2$ID, ]
+
+data2 <- data2[data2$ID %in% consumedsum2$ID, ]
+
+consumedsum2 <- consumedsum2[order(consumedsum2$ID), ]
+
+data2$area <- consumedsum2$totalarea
+```
+
+Let's try it now
+
+```{r}
+modcomb <- lmer(area ~ mass.max + (1|bin), data = data2)
+
+summary(modcomb)
+```

### 2020-12-05 ASNCode.Rmd
New document for code for ASN talk

---
title: "Code for Graphs for ASN presentation"
output: html_notebook
---
This document contains the code for the graphs I'll include in my 2021 ASN presentation, as well as model results I'll present.

As such, it doesn't contain all models or all graphs - see WorkingScript.Rmd for a stream-of-consciousness view of my work.

## Load in packages

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(lme4)
library(lubridate)
library(viridisLite)
```

## Load in data

```{r}
data <- read.csv("~/Desktop/MsCcHSFeedNov30modfinal.csv")
scan <- read.csv("~/Desktop/MsCcHSFeedLeafScanFinal.csv", header = T)
```

## Manipulate data into correct forms

```{r}
data <- data[data$fate != "dead" & data$fate != "quink" & data$fate != "wander*" & data$fate != "?", ]
```

```{r}
#1
scan$comb <- paste(scan$Caterpillar.ID, "_", scan$Leaf.ID)

#0
unique <- unique(scan$comb)
consumed <- as.data.frame(unique)
consumed$area <- 0

#2-4
for (i in 1:length(consumed$unique)){
    subset <- filter(scan, scan$comb == consumed[i, 1])
    value <- max(subset$Leaf.Area) - min(subset$Leaf.Area)
    consumed[i, 2] <- value
}

#5
consumed <- consumed %>%
  separate(unique, c("catID", "leafID"), "_")

#6
ID <- unique(consumed$catID)
consumedsum <- as.data.frame(ID)
consumedsum$totalarea <- 0

#7
for (i in 1:length(consumedsum$ID)){
  subset2 <- filter(consumed, consumed$catID == consumedsum[i, 1])
  value2 <- sum(subset2$area)
  consumedsum[i, 2] <- value2
}

#8
consumedsum$ID <- as.numeric(consumedsum$ID)

consumedsum <- consumedsum[consumedsum$ID %in% data$ID, ]

data <- data[data$ID %in% consumedsum$ID, ]

consumedsum <- consumedsum[order(consumedsum$ID), ]

data$area <- consumedsum$totalarea

```

```{r}
# Internal process of the loop to convert days to dates
expt_day <- function(start.date, date){
  date <- mdy(date)
  start <- mdy(start.date)
  diff <- yday(date) - yday(start)

  return(diff)
}

# Code for the loop itself
loop <- function(start.date, date.list){
  days <- rep(NA, length(date.list))
  for (i in 1:(length(days))){
    days[i] <- expt_day(start.date = start.date, date = date.list[i])
  }
  return(days)
}
```

```{r}
data$day.hatch <- loop(start.date = "07/12/2020", date.list = data$date.hatch)
data$day.max <- loop(start.date = "07/12/2020", date.list = data$date.max)

data$ttmax <- data$day.max - data$day.hatch
```

## Graphs

```{r}
TBdata <- data[data$food == "TB", ]
DCdata <- data[data$food == "DC", ]
```

Four colors I'm using:

emerged: #66CB5D
wander: #21908D
wowe: #3E4F8A
wowe mongo: #450F57

### Maximum mass gained and age at that point

```{r}
ggplot(aes(x = ttmax, y = mass.max, color = fate), data = DCdata) +
  theme_bw() + 
  geom_point(alpha = 0.8) + 
  scale_color_manual(values = c("#66CB5D", "#21908D", "#3E4F8A", "#450F57")) + 
  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (mg)")
```

### 2020-12-07 ASNCode.Rmd
Changed some colors, added some graphs

@@
 wowe: #3E4F8A
-wowe mongo: #450F57
+wowe mongo: #450D54
+
+### Wasp fate
 
@@
   geom_point(alpha = 0.8) + 
-  scale_color_manual(values = c("#66CB5D", "#21908D", "#3E4F8A", "#450F57")) + 
-  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (mg)")
+  scale_color_manual(values = c("#66CB5D", "#21908D", "#3E4F8A", "#450D54")) + 
+  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (mg)", 
+       color = "Developmental Outcome")
 ```
+
+```{r}
+dataPHS <- data[data$treatment == "P HS", ]
+
+ggplot(aes(x = ttmax, y = mass.max, color = fate), data = dataPHS) +
+  theme_bw() + 
+  geom_point(alpha = 0.8) + 
+  scale_color_manual(values = c("#66CB5D", "#21908D", "#3E4F8A", "#450D54")) + 
+  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (mg)", 
+       color = "Developmental Outcome")
+```
+
+### Maximum mass compared to plant matter consumed
+
+```{r}
+ggplot(aes(x = area, y = mass.max), data = DCdata) + 
+  theme_bw() + 
+  geom_point(aes(color = fate)) + 
+  scale_color_manual(values = c("#66CB5D", "#21908D", "#3E4F8A", "#450D54")) +
+  labs(x = "Leaf surface area consumed (cm2)", y = "Maximum mass achieved (mg)",
+       color = "Developmental Outcome")
+```
+```{r}
+
+```

### 2020-12-13 ASNCode.Rmd
Adjusted some graphs

@@
 ```{r}
-ggplot(aes(x = ttmax, y = mass.max, color = fate), data = DCdata) +
+ggplot(aes(x = ttmax, y = mass.max, color = fate, shape = food), data = data) +
   theme_bw() + 
   geom_point(alpha = 0.8) + 
+  scale_shape_manual(values = c(19, 6)) + 
   scale_color_manual(values = c("#66CB5D", "#21908D", "#3E4F8A", "#450D54")) + 
   labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (mg)", 
-       color = "Developmental Outcome")
+       color = "Developmental Outcome", shape = "Hostplant Consumed")
 ```
@@
 ```{r}
-ggplot(aes(x = area, y = mass.max), data = DCdata) + 
+ggplot(aes(x = area, y = mass.max), data = data) + 
   theme_bw() + 
-  geom_point(aes(color = fate)) + 
+  geom_point(aes(color = fate, shape = food)) + 
+  scale_shape_manual(values = c(19, 6)) + 
   scale_color_manual(values = c("#66CB5D", "#21908D", "#3E4F8A", "#450D54")) +
   labs(x = "Leaf surface area consumed (cm2)", y = "Maximum mass achieved (mg)",
-       color = "Developmental Outcome")
+       color = "Developmental Outcome", shape = "Hostplant Consumed")
 ```

### 2020-12-17 ASNCode.Rmd
Changed graphs to 3 outcomes, rather than 4. Changed colors, added wasp graph

--- 2020-12-07 ASNCode.Rmd
@@
 ```{r}
-data <- read.csv("~/Desktop/MsCcHSFeedNov30modfinal.csv")
+data <- read.csv("~/Desktop/MsCcHSFeedDec14final.csv")
 scan <- read.csv("~/Desktop/MsCcHSFeedLeafScanFinal.csv", header = T)
@@
 data <- data[data$fate != "dead" & data$fate != "quink" & data$fate != "wander*" & data$fate != "?", ]
+
+data$outcome <- data$fate
+
+data$outcome <- gsub(" mongo", "", data$outcome)
+data$outcome <- gsub("em", "we", data$outcome)
+
 ```
@@
 
+```{r}
+data$perc.w.ecl <- data$num.w.eclos / (data$num.w.coc + data$num.w.larvae)
+data$num.w.total <- (data$num.w.coc + data$num.w.larvae)
+
+data$HS <- factor(data$HS, levels = c("yes", "no"))
+```
+
 ## Graphs
@@
 
-Four colors I'm using:
+Three colors I'm using:
 
-emerged: #66CB5D
-wander: #21908D
-wowe: #3E4F8A
-wowe mongo: #450D54
+("#66CB5D", "#21908D", "#3E4F8A", "#450D54")
+("#460F5A", "#87D548", "#30B67B")
+
+wander: #882255
+we: #88CCEE
+wowe: #117733
 
 ### Wasp fate
+
+```{r}
+ggplot(aes(x = num.w.total, y = perc.w.ecl, color = HS), data = data) + 
+  theme_bw() + 
+  geom_smooth(method = "lm", se = F) +
+  geom_point(alpha = 0.8, aes(shape = food)) + 
+  scale_shape_manual(values = c(19, 6)) +
+  scale_color_manual(values = c("#EF000D", "#00CFD2")) + 
+  labs(x = "Number of wasps emerged", y = "Percentage of wasps eclosed", shape = "Hostplant Consumed", 
+       color = "Heat Shock Status")
+```
 
@@
 ```{r}
-ggplot(aes(x = ttmax, y = mass.max, color = fate), data = DCdata) +
+ggplot(aes(x = ttmax, y = mass.max, color = outcome, shape = food), data = data) +
   theme_bw() + 
   geom_point(alpha = 0.8) + 
-  scale_color_manual(values = c("#66CB5D", "#21908D", "#3E4F8A", "#450D54")) + 
+  scale_shape_manual(values = c(19, 6)) + 
+  scale_color_manual(values = c("#882255", "#88CCEE", "#117733")) + 
   labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (mg)", 
-       color = "Developmental Outcome")
+       color = "Developmental Outcome", shape = "Hostplant Consumed")
 ```
@@
 ```{r}
-ggplot(aes(x = area, y = mass.max), data = DCdata) + 
+ggplot(aes(x = area, y = mass.max), data = data) + 
   theme_bw() + 
-  geom_point(aes(color = fate)) + 
-  scale_color_manual(values = c("#66CB5D", "#21908D", "#3E4F8A", "#450D54")) +
+  geom_point(aes(color = outcome, shape = food)) + 
+  scale_shape_manual(values = c(19, 6)) + 
+  scale_color_manual(values = c("#882255", "#88CCEE", "#117733")) +
   labs(x = "Leaf surface area consumed (cm2)", y = "Maximum mass achieved (mg)",
-       color = "Developmental Outcome")
+       color = "Developmental Outcome", shape = "Hostplant Consumed")
 ```
-```{r}
-
-```

### 2020-12-21 ASNCode.Rmd
New dataset, adjusted axis title

@@
 ```{r}
-data <- read.csv("~/Desktop/MsCcHSFeedDec14final.csv")
+data <- read.csv("~/Desktop/MsCcHSFeedDec19final.csv")
 scan <- read.csv("~/Desktop/MsCcHSFeedLeafScanFinal.csv", header = T)
@@
   theme_bw() + 
+  ylim(0, 1.05) + 
   geom_smooth(method = "lm", se = F) +
@@
   scale_color_manual(values = c("#EF000D", "#00CFD2")) + 
-  labs(x = "Number of wasps emerged", y = "Percentage of wasps eclosed", shape = "Hostplant Consumed", 
+  labs(x = "Number emerged", y = "Percentage of wasps eclosed", shape = "Hostplant Consumed", 
        color = "Heat Shock Status")

### 2020-12-27 ASNCode.Rmd
Redid caterpillar figures

@@
 ```{r}
-data <- read.csv("~/Desktop/MsCcHSFeedDec19final.csv")
+data <- read.csv("~/Desktop/MsCcHSFeedDec27Final.csv")
 scan <- read.csv("~/Desktop/MsCcHSFeedLeafScanFinal.csv", header = T)
@@
 data$outcome <- gsub("em", "we", data$outcome)
+
+data$mass.max <- data$mass.max / 1000
 
@@
 data$HS <- factor(data$HS, levels = c("yes", "no"))
+data$para <- factor(data$para, levels = c("yes", "no"))
 ```
+
+## Graphs
+
+### Wasp fate
+
+```{r}
+ggplot(aes(x = num.w.total, y = perc.w.ecl, color = food), data = data) + 
+  theme_bw() + 
+  ylim(0, 1.05) + 
+  geom_point(aes(shape = treatment)) + 
+  scale_shape_manual(values = c(19, 1, 17, 2)) +
+  labs(x = "Number emerged", y = "Percentage of wasps eclosed", color = "Hostplant Consumed", 
+       shape = "Heat Shock Status")
+```
+
+### Maximum mass gained and age at that point
+
+```{r}
+ggplot(aes(x = ttmax, y = mass.max, color = food, shape = treatment), 
+       data = data[data$para == "no", ]) +
+  theme_bw() + 
+  ylim(0, 20) + 
+  xlim(15, 45) + 
+  geom_point() + 
+  scale_shape_manual(values = c(19, 1, 17, 2)) + 
+  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (g)", 
+       shape = "Treatment", color = "Hostplant Consumed")
+
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/ASN1.png", width = 8, height = 5)
+```
+
+```{r}
+ggplot(aes(x = ttmax, y = mass.max, color = food, shape = treatment), 
+       data = data[data$treatment != "P HS", ]) +
+  theme_bw() + 
+  ylim(0, 20) + 
+  xlim(15, 45) + 
+  geom_point() + 
+  scale_shape_manual(values = c(19, 1, 2)) + 
+  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (g)", 
+       shape = "Treatment", color = "Hostplant Consumed")
+
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/ASN2.png", width = 8, height = 5)
+```
+
+```{r}
+ggplot(aes(x = ttmax, y = mass.max, color = food, shape = treatment), data = data) +
+  theme_bw() + 
+  ylim(0, 20) + 
+  xlim(15, 45) + 
+  geom_point() + 
+  scale_shape_manual(values = c(19, 1, 17, 2)) + 
+  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (g)", 
+       shape = "Treatment", color = "Hostplant Consumed")
+
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/ASN3.png", width = 8, height = 5)
+```
+
+# ----- ARCHIVE ----- DO NOT RUN -----
 

### 2020-12-27 ASNCode.Rmd
fixed leaf area graphs

@@
 
-### Wasp fate
-
-```{r}
-ggplot(aes(x = num.w.total, y = perc.w.ecl, color = food), data = data) + 
-  theme_bw() + 
-  ylim(0, 1.05) + 
-  geom_point(aes(shape = treatment)) + 
-  scale_shape_manual(values = c(19, 1, 17, 2)) +
-  labs(x = "Number emerged", y = "Percentage of wasps eclosed", color = "Hostplant Consumed", 
-       shape = "Heat Shock Status")
-```
-
 ### Maximum mass gained and age at that point
@@
 ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/ASN3.png", width = 8, height = 5)
+```
+
+### Maximum mass compared to plant matter consumed
+
+```{r}
+ggplot(aes(x = area, y = mass.max, color = food, shape = treatment), 
+       data = data[data$para == "no", ]) + 
+  theme_bw() + 
+  xlim(0, 6000) + 
+  ylim(0, 20) + 
+  geom_point() + 
+  scale_shape_manual(values = c(19, 1, 17, 2)) + 
+  labs(x = "Leaf surface area consumed (cm2)", y = "Maximum mass achieved (mg)",
+       shape = "Treatment", color = "Hostplant Consumed")
+
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/ASN4.png", width = 8, height = 5)
+```
+
+```{r}
+ggplot(aes(x = area, y = mass.max, color = food, shape = treatment), 
+       data = data[data$treatment != "P HS", ]) + 
+  theme_bw() + 
+  xlim(0, 6000) + 
+  ylim(0, 20) + 
+  geom_point() + 
+  scale_shape_manual(values = c(19, 1, 2)) + 
+  labs(x = "Leaf surface area consumed (cm2)", y = "Maximum mass achieved (mg)",
+       shape = "Treatment", color = "Hostplant Consumed")
+
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/ASN5.png", width = 8, height = 5)
+```
+
+```{r}
+ggplot(aes(x = area, y = mass.max, color = food, shape = treatment), data = data) + 
+  theme_bw() + 
+  xlim(0, 6000) + 
+  ylim(0, 20) + 
+  geom_point() + 
+  scale_shape_manual(values = c(19, 1, 17, 2)) + 
+  labs(x = "Leaf surface area consumed (cm2)", y = "Maximum mass achieved (mg)",
+       shape = "Treatment", color = "Hostplant Consumed")
+
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/ASN6.png", width = 8, height = 5)
+```
+
+### Wasp fate
+
+```{r}
+ggplot(aes(x = num.w.total, y = perc.w.ecl, color = food), data = data) + 
+  theme_bw() + 
+  ylim(0, 1.05) + 
+  geom_point(aes(shape = treatment)) + 
+  scale_shape_manual(values = c(19, 1, 17, 2)) +
+  labs(x = "Number emerged", y = "Percentage of wasps eclosed", color = "Hostplant Consumed", 
+       shape = "Heat Shock Status")
+
 ```

### 2021-01-02 ASNCode.Rmd
Fixed wasp graph
Fixed input file, redid relevant graphs

@@
 ```{r}
-data <- read.csv("~/Desktop/MsCcHSFeedDec27Final.csv")
+data <- read.csv("~/Desktop/MsCcHSFeedJan1MOD.csv")
 scan <- read.csv("~/Desktop/MsCcHSFeedLeafScanFinal.csv", header = T)
@@
 data <- data[data$fate != "dead" & data$fate != "quink" & data$fate != "wander*" & data$fate != "?", ]
+data <- data[complete.cases(data[, 1]), ]
 
@@
 
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/ASN7.png", width = 8, height = 5)
 ```

### 2021-01-10 ASNCode.Rmd
Fixed axes

--- 2020-12-27 ASNCode.Rmd
@@
 ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/ASN3.png", width = 8, height = 5)
+```
+
+### Maximum mass compared to plant matter consumed
+
+```{r}
+ggplot(aes(x = area, y = mass.max, color = food, shape = treatment), 
+       data = data[data$para == "no", ]) + 
+  theme_bw() + 
+  xlim(0, 6000) + 
+  ylim(0, 20) + 
+  geom_point() + 
+  scale_shape_manual(values = c(19, 1, 17, 2)) + 
+  labs(x = "Leaf surface area consumed (cm2)", y = "Maximum mass achieved (g)",
+       shape = "Treatment", color = "Hostplant Consumed")
+
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/ASN4.png", width = 8, height = 5)
+```
+
+```{r}
+ggplot(aes(x = area, y = mass.max, color = food, shape = treatment), 
+       data = data[data$treatment != "P HS", ]) + 
+  theme_bw() + 
+  xlim(0, 6000) + 
+  ylim(0, 20) + 
+  geom_point() + 
+  scale_shape_manual(values = c(19, 1, 2)) + 
+  labs(x = "Leaf surface area consumed (cm2)", y = "Maximum mass achieved (g)",
+       shape = "Treatment", color = "Hostplant Consumed")
+
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/ASN5.png", width = 8, height = 5)
+```
+
+```{r}
+ggplot(aes(x = area, y = mass.max, color = food, shape = treatment), data = data) + 
+  theme_bw() + 
+  xlim(0, 6000) + 
+  ylim(0, 20) + 
+  geom_point() + 
+  scale_shape_manual(values = c(19, 1, 17, 2)) + 
+  labs(x = "Leaf surface area consumed (cm2)", y = "Maximum mass achieved (g)",
+       shape = "Treatment", color = "Hostplant Consumed")
+
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/ASN6.png", width = 8, height = 5)
+```
+
+### Wasp fate
+
+```{r}
+ggplot(aes(x = num.w.total, y = perc.w.ecl, color = food), data = data) + 
+  theme_bw() + 
+  ylim(0, 1.05) + 
+  geom_point(aes(shape = treatment)) + 
+  scale_shape_manual(values = c(19, 1, 17, 2)) +
+  labs(x = "Number of wasp larvae emerged", y = "Proportion of wasps eclosed", color = "Hostplant Consumed", 
+       shape = "Heat Shock Status")
+
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/ASN7.png", width = 8, height = 5)
 ```

### 2021-03-15 ASNCodeUpdatedFigs.Rmd
Deleted archive of old graphs

--- 2021-01-10 ASNCode.Rmd
@@
 ```
-
-# ----- ARCHIVE ----- DO NOT RUN -----
-
-## Graphs
-
-```{r}
-TBdata <- data[data$food == "TB", ]
-DCdata <- data[data$food == "DC", ]
-```
-
-Three colors I'm using:
-
-("#66CB5D", "#21908D", "#3E4F8A", "#450D54")
-("#460F5A", "#87D548", "#30B67B")
-
-wander: #882255
-we: #88CCEE
-wowe: #117733
-
-### Wasp fate
-
-```{r}
-ggplot(aes(x = num.w.total, y = perc.w.ecl, color = HS), data = data) + 
-  theme_bw() + 
-  ylim(0, 1.05) + 
-  geom_smooth(method = "lm", se = F) +
-  geom_point(alpha = 0.8, aes(shape = food)) + 
-  scale_shape_manual(values = c(19, 6)) +
-  scale_color_manual(values = c("#EF000D", "#00CFD2")) + 
-  labs(x = "Number emerged", y = "Percentage of wasps eclosed", shape = "Hostplant Consumed", 
-       color = "Heat Shock Status")
-```
-
-### Maximum mass gained and age at that point
-
-```{r}
-ggplot(aes(x = ttmax, y = mass.max, color = outcome, shape = food), data = data) +
-  theme_bw() + 
-  geom_point(alpha = 0.8) + 
-  scale_shape_manual(values = c(19, 6)) + 
-  scale_color_manual(values = c("#882255", "#88CCEE", "#117733")) + 
-  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (mg)", 
-       color = "Developmental Outcome", shape = "Hostplant Consumed")
-```
-
-```{r}
-dataPHS <- data[data$treatment == "P HS", ]
-
-ggplot(aes(x = ttmax, y = mass.max, color = fate), data = dataPHS) +
-  theme_bw() + 
-  geom_point(alpha = 0.8) + 
-  scale_color_manual(values = c("#66CB5D", "#21908D", "#3E4F8A", "#450D54")) + 
-  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (mg)", 
-       color = "Developmental Outcome")
-```
-
-### Maximum mass compared to plant matter consumed
-
-```{r}
-ggplot(aes(x = area, y = mass.max), data = data) + 
-  theme_bw() + 
-  geom_point(aes(color = outcome, shape = food)) + 
-  scale_shape_manual(values = c(19, 6)) + 
-  scale_color_manual(values = c("#882255", "#88CCEE", "#117733")) +
-  labs(x = "Leaf surface area consumed (cm2)", y = "Maximum mass achieved (mg)",
-       color = "Developmental Outcome", shape = "Hostplant Consumed")
-```

### 2021-03-15 ASNCodeUpdatedFigs.Rmd
Got first graph working, after new data manipulation

@@
 library(viridisLite)
+library(Rmisc)
 ```
@@
 
-data$outcome <- gsub(" mongo", "", data$outcome)
+#data$outcome <- gsub(" mongo", "", data$outcome)
 data$outcome <- gsub("em", "we", data$outcome)
@@
 
-## Graphs
+## Get means for data
+
+```{r}
+datalong <- data %>%
+  select(ID, food, fate, mass.max, ttmax, area)
+
+meantime <- summarySE(datalong, measurevar = "ttmax", groupvars = c("food", "fate"), na.rm = TRUE)
+
+meanmass <- summarySE(datalong, measurevar = "mass.max", groupvars = c("food", "fate"), na.rm = TRUE)
+
+meanarea <- summarySE(datalong, measurevar = "area", groupvars = c("food", "fate"), na.rm = TRUE)
+```
+
+### Group them into one dataframe
+
+```{r}
+datameans <- meantime %>%
+  select(food, fate, ttmax, se)
+
+datameans$mass.max <- meanmass$mass.max
+datameans$semass <- meanmass$se
+datameans$area <- meanarea$area
+datameans$searea <- meanarea$se
+
+```
+
+## Graphs with means only
+
+### Maximum mass gained and age at that point
+
+```{r}
+ggplot(aes(x = ttmax, y = mass.max, color = food, shape = fate), 
+       data = datameans) + 
+  theme_bw() + 
+  ylim(0, 20) + 
+  xlim(15, 45) +
+  geom_point(size = 3) + 
+  scale_shape_manual(values = c(5, 2, 1, 19)) + 
+  geom_errorbar(aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
+  geom_errorbarh(aes(xmin = ttmax - se, xmax = ttmax + se), size = .5) + 
+  guides(size = FALSE) + 
+  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (g)", 
+       shape = "Developmental Outcome", color = "Hostplant Consumed")
+```
+
+## Graphs with all datapoints
 

### 2021-03-15 ASNCodeUpdatedFigs.Rmd
Got second graph, saved versions of the graphs as images

@@
   xlim(15, 45) +
-  geom_point(size = 3) + 
+  geom_point(size = 4) + 
   scale_shape_manual(values = c(5, 2, 1, 19)) + 
@@
        shape = "Developmental Outcome", color = "Hostplant Consumed")
+
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/meantime.png", width = 8, height = 5)
+```
+
+### Maximum mass compared to plant matter consumed
+
+```{r}
+ggplot(aes(x = area, y = mass.max, color = food, shape = fate), 
+       data = datameans) + 
+  theme_bw() + 
+  ylim(0, 20) + 
+  xlim(0, 6000) +
+  geom_point(size = 4) + 
+  scale_shape_manual(values = c(5, 2, 1, 19)) + 
+  geom_errorbar(aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
+  geom_errorbarh(aes(xmin = area - searea, xmax = area + searea), size = .5) + 
+  guides(size = FALSE) + 
+  labs(x = "Hostplant leaf area consumed (cm^2)", y = "Maximum mass achieved (g)", 
+       shape = "Developmental Outcome", color = "Hostplant Consumed")
+
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/meanarea.png", width = 8, height = 5)
 ```

### 2022-01-01 ArchivedCode/MsCcHSFeedOutlineDec1.Rmd
Uploaded past scripts from the outline

---
title: "MsCcHSFeed Outline"
output: html_notebook
---

```{r}
library(ggplot2)
library(tidyverse)
library(Rmisc)
```

```{r}
data <- read.csv("~/Desktop/MsCcHSFeedJan1MOD.csv")
scan <- read.csv("~/Desktop/MsCcHSFeedLeafScanFinal.csv", header = T)
```

```{r}
data <- data[data$fate != "dead" & data$fate != "quink" & data$fate != "wander*" & data$fate != "?", ]
data <- data[complete.cases(data[, 1]), ]

```

```{r}
datadead <- read.csv("~/Desktop/MsCcHSFeedJan1MOD.csv")
datadead <- datadead[datadead$fate != "quink" & datadead$fate != "wander*" & datadead$fate != "?", ]
datadead <- datadead[complete.cases(datadead[, 1]), ]
datadead$treatment <- factor(datadead$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
```

# Fig 1: Counts

```{r}
count(datadead[datadead$food == "TB" & datadead$para == "yes" & datadead$HS == "yes", ])
count(datadead[datadead$food == "TB" & datadead$para == "yes" & datadead$HS == "no", ])
count(datadead[datadead$food == "TB" & datadead$para == "no" & datadead$HS == "yes", ])
count(datadead[datadead$food == "TB" & datadead$para == "no" & datadead$HS == "no", ])
```

```{r}
count(datadead[datadead$food == "DC" & datadead$para == "yes" & datadead$HS == "yes", ])
count(datadead[datadead$food == "DC" & datadead$para == "yes" & datadead$HS == "no", ])
count(datadead[datadead$food == "DC" & datadead$para == "no" & datadead$HS == "yes", ])
count(datadead[datadead$food == "DC" & datadead$para == "no" & datadead$HS == "no", ])
```

# Fig 2: Violin plots of max mass

```{r}
data$treatment <- factor(data$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
dataviolin <- data
dataviolin$fate <- gsub(" mongo", "", dataviolin$fate)

violins <- ggplot(data = dataviolin, aes(x = treatment, y = mass.max)) + 
  geom_violin(fill = "light grey", color = "light grey") + 
  geom_jitter(aes(color = fate), width = 0.1, height = 0) + 
  theme_bw() + 
  labs(x = "Treatment Group", y  = "Maximum mass achieved (mg)",  color = "Developmental Outcome") + 
  scale_color_manual(values = c("#1E88E5", "lime green", "#D81B60"), 
                     labels = c("WE", "Wander", "WOWE"))

violins

ggsave("~/Desktop/violins2.png", violins, width = 8, height = 5)

```

# Fig 3: Developmental outcome proportions

## Make graph of outcomes

```{r}
data$treatment <- factor(data$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
```

## This time, keep the dead

```{r}
barsdead <- ggplot(data = datadead, aes(x = treatment, fill = fate)) + 
  theme_bw() + 
  geom_bar(position = "fill") + 
  facet_wrap(~food) + 
  labs(x = "Treatment group", y = "Proportion of indiviudals", fill = "Developmental Outcome") + 
  scale_fill_manual(values = c("purple", "#1E88E5", "lime green", "orange", "#D81B60"),
                    labels = c("Died", "WE", "Wander", "WOWE", "WOWE mongo"))

barsdead

ggsave("~/Desktop/outcomesdead.png", plot = barsdead, width = 8, height = 5)
```

# Fig 4: Maximum mass and age

```{r}
newmeans <- ggplot(data = datalong5, aes(x = ttmax, y = mass.max, color = fate, shape = food)) + 
  theme_bw() + 
  xlim(15, 45) +
  geom_point(alpha = 0.4) + 
  scale_shape_manual(values = c(1, 19)) + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
                     labels = c("WE", "Wander", "WOWE", "WOWE mongo")) + 
  geom_point(aes(x = ttmax, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
  geom_errorbarh(data = datameans2, aes(xmin = ttmax - se, xmax = ttmax + se), size = .5) + 
  guides(size = FALSE) + 
  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (mg)", 
       shape = "Hostplant Consumed", color = "Developmental Outcome")

newmeans

ggsave("~/Desktop/newmeans.png", newmeans, width = 8, height = 5)
```

## Stats

### Maximum age differences across treatment and outcome

```{r}
maxage <- lmer(ttmax ~ fate*food + (1|bin), data = data)

anova(maxage)
```

```{r}
maxage2 <- lmer(ttmax ~ fate + food + (1|bin), data = data)

anova(maxage2)
```

```{r}
AIC(maxage, maxage2)
```

### Maximum mass

```{r}
maxmass <- lmer(mass.max ~ fate*food + (1|bin), data = data)

anova(maxmass)
```

# Fig 5: Leaf matter consumed vs. max mass

```{r}
#1
scan$comb <- paste(scan$Caterpillar.ID, "_", scan$Leaf.ID)

#0
unique <- unique(scan$comb)
consumed <- as.data.frame(unique)
consumed$area <- 0

#2-4
for (i in 1:length(consumed$unique)){
    subset <- filter(scan, scan$comb == consumed[i, 1])
    value <- max(subset$Leaf.Area) - min(subset$Leaf.Area)
    consumed[i, 2] <- value
}

#5
consumed <- consumed %>%
  separate(unique, c("catID", "leafID"), "_")

#6
ID <- unique(consumed$catID)
consumedsum <- as.data.frame(ID)
consumedsum$totalarea <- 0

#7
for (i in 1:length(consumedsum$ID)){
  subset2 <- filter(consumed, consumed$catID == consumedsum[i, 1])
  value2 <- sum(subset2$area)
  consumedsum[i, 2] <- value2
}

#8
consumedsum$ID <- as.numeric(consumedsum$ID)

consumedsum <- consumedsum[consumedsum$ID %in% data$ID, ]

data <- data[data$ID %in% consumedsum$ID, ]

consumedsum <- consumedsum[order(consumedsum$ID), ]

data$area <- consumedsum$totalarea

```

```{r}
datalong5 <- data %>%
  select(ID, food, fate, mass.max, ttmax, area)

meantime2 <- summarySE(datalong5, measurevar = "ttmax", groupvars = c("food", "fate"), na.rm = TRUE)

meanmass2 <- summarySE(datalong5, measurevar = "mass.max", groupvars = c("food", "fate"), na.rm = TRUE)

meanarea2 <- summarySE(datalong5, measurevar = "area", groupvars = c("food", "fate"), na.rm = TRUE)
```

### Group them into one dataframe

```{r}
datameans2 <- meantime2 %>%
  select(food, fate, ttmax, se)

datameans2$mass.max <- meanmass2$mass.max
datameans2$semass <- meanmass2$se
datameans2$area <- meanarea2$area
datameans2$arease <- meanarea2$se

```

```{r}
newarea <- ggplot(data = datalong5, aes(x = area, y = mass.max, color = fate, shape = food)) + 
  theme_bw() + 
  geom_point(alpha = 0.4) + 
  scale_shape_manual(values = c(1, 19)) + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
                     labels = c("WE", "Wander", "WOWE", "WOWE mongo")) + 
  ylim(0, 20000) + 
  xlim(0, 6000) +
  geom_point(aes(x = area, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
  geom_errorbarh(data = datameans2, aes(xmin = area - arease, xmax = area + arease), size = .5) + 
  guides(size = FALSE) + 
  labs(x = "Hostplant leaf area consumed (cm^2)", y = "Maximum mass achieved (mg)", 
       shape = "Hostplant Consumed", color = "Developmental Outcome")

newarea

ggsave("~/Desktop/newarea.png", newarea, width = 8, height = 5)
```

## Stats

```{r}
areatrt <- lmer(area ~ fate*food + (1|bin), data = data)

anova(areatrt)
```

# Growth trajectories of different treatment groups 
## Manipulate the data
```{r}
# Internal process of the loop to convert days to dates
expt_day <- function(start.date, date){
  date <- mdy(date)
  start <- mdy(start.date)
  diff <- yday(date) - yday(start)

  return(diff)
}

# Code for the loop itself
loop <- function(start.date, date.list){
  days <- rep(NA, length(date.list))
  for (i in 1:(length(days))){
    days[i] <- expt_day(start.date = start.date, date = date.list[i])
  }
  return(days)
}
```

```{r}
data$day.hatch <- loop(start.date = "07/12/2020", date.list = data$date.hatch)
data$day.3rd <- loop(start.date = "07/12/2020", date.list = data$date.3rd)
data$day.4th <- loop(start.date = "07/12/2020", date.list = data$date.4th)
data$day.5th <- loop(start.date = "07/12/2020", date.list = data$date.5th)
data$day.w <- loop(start.date = "07/12/2020", date.list = data$date.w)

data$day.5th.2 <- loop(start.date = "07/12/2020", date.list = data$date.5th.2)
data$day.5th.3 <- loop(start.date = "07/12/2020", date.list = data$date.5th.3)
data$day.6th <- loop(start.date = "07/12/2020", date.list = data$date.6th)
data$day.6th.2 <- loop(start.date = "07/12/2020", date.list = data$date.6th.2)
data$day.6th.3 <- loop(start.date = "07/12/2020", date.list = data$date.6th.3)
data$day.7th <- loop(start.date = "07/12/2020", date.list = data$date.7th)
data$day.7th.2 <- loop(start.date = "07/12/2020", date.list = data$date.7th.2)
data$day.7th.3 <- loop(start.date = "07/12/2020", date.list = data$date.7th.3)
data$day.coc <- loop(start.date = "07/12/2020", date.list = data$date.coc)

data$tthatch <- 0
data$tt3rd <- data$day.3rd - data$day.hatch
data$tt4th <- data$day.4th - data$day.hatch
data$tt5th <- data$day.5th - data$day.hatch
data$ttw <- data$day.w - data$day.hatch

data$tt5th.2 <- data$day.5th.2 - data$day.hatch
data$tt5th.3 <- data$day.5th.3 - data$day.hatch
data$tt6th <- data$day.6th - data$day.hatch
data$tt6th.2 <- data$day.6th.2 - data$day.hatch
data$tt6th.3 <- data$day.6th.3 - data$day.hatch
data$tt7th <- data$day.7th - data$day.hatch
data$tt7th.2 <- data$day.7th.2 - data$day.hatch
data$tt7th.3 <- data$day.7th.3 - data$day.hatch
data$ttcoc <- data$day.coc - data$day.hatch

```

```{r}
data$ln.hatch <- log(data$mass.hatch)
data$ln.3rd <- log(data$mass.3rd)
data$ln.4th <- log(data$mass.4th)
data$ln.5th <- log(data$mass.5th)
data$ln.w <- log(data$mass.w)

data$ln.5th.2 <- log(data$mass.5th.2)
data$ln.5th.3 <- log(data$mass.5th.3)
data$ln.6th <- log(data$mass.6th)
data$ln.6th.2 <- log(data$mass.6th.2)
data$ln.6th.3 <- log(data$mass.6th.3)
data$ln.7th <- log(data$mass.7th)
data$ln.7th.2 <- log(data$mass.7th.2)
data$ln.7th.3 <- log(data$mass.7th.3)
data$ln.coc <- log(data$mass.remove)

```

```{r}
dataslim <- data[data$treatment == "NP NHS" | data$treatment == "NP HS", ] %>%
  select(ID, food, fate, treatment, tthatch, ln.hatch, tt3rd, ln.3rd, tt4th, ln.4th, tt5th, ln.5th, ttw, ln.w)

dataslim2 <- data[data$treatment == "P NHS" | data$treatment == "P HS", ] %>%
  select(ID, food, fate, treatment, tthatch, ln.hatch, tt3rd, ln.3rd, tt4th, ln.4th, tt5th, ln.5th, tt5th.2, 
         ln.5th.2, tt5th.3, ln.5th.3, tt6th, ln.6th, tt6th.2, ln.6th.2, tt6th.3, ln.6th.3, tt7th, ln.7th, 
         tt7th.2, ln.7th.2, tt7th.3, ln.7th.3, ttcoc, ln.coc )
```

## NP NHS vs NP HS

### More manupulation

```{r}
masslong <- dataslim %>%
  gather(instar, mass, ln.hatch, ln.3rd, ln.4th, ln.5th, ln.w)
masslong$instar <- gsub("ln.", "", masslong$instar)

agelong <- dataslim %>%
  gather(instar, age, tthatch, tt3rd, tt4th, tt5th, ttw)
agelong$instar <- gsub("tt", "", agelong$instar)

masslong <- masslong %>% 
  select(ID, treatment, food, instar, mass)
agelong <- agelong %>% 
  select(ID, treatment, food, instar, age)

datalong<-merge(masslong, agelong, by=c("ID", "treatment", "food", "instar"))

datalong$instar <- factor(datalong$instar, levels = c("hatch", "3rd", "4th", "5th", "w"))

datalong$newtreatment <- paste(datalong$treatment, datalong$food)
datalong$newtreatment <- factor(datalong$newtreatment, levels = c("NP NHS DC", "NP NHS TB", "NP HS DC", "NP HS TB"))
```

```{r}

#calculate means and variation

#constructing summarySE for age and mass to make mean plot

masssum <- summarySE(datalong, measurevar = "mass",
                  groupvars = c("newtreatment", "instar"),
                  na.rm=TRUE)
masssum

agesum <- summarySE(datalong, measurevar = "age",
                   groupvars = c("newtreatment", "instar"),
                   na.rm = TRUE)
agesum

#combine into one data frame

masssum$age <- agesum[, 4]
masssum$age.se <- agesum[, 6]
masssum$age.ci <- agesum[, 7]
```

### Plot the data (with CIs)

```{r}
meanplot <- ggplot(masssum, aes(x = age, y = mass, group = newtreatment, color = newtreatment, shape= newtreatment)) + 
  theme_bw() + 
  geom_point(size = 4) + 
  geom_line(aes(linetype = newtreatment), size = 1) + 
  geom_errorbar(aes(ymin = mass-(ci/2), ymax = mass + (ci/2)),
                width = .3, size = 1) + 
  geom_errorbarh(aes(xmin = age - (age.ci/2), xmax = age + (age.ci/2)),
                 height = .3, size = 1) + 
  scale_color_manual(values = c("#D81B60","#1E88E5", "#D81B60","#1E88E5" )) +
  scale_shape_manual(values = c(1, 1, 2, 2)) + 
  scale_linetype_manual(values = c("dashed", "dashed", "solid", "solid")) + 
  labs(x = "Total developmental age (days)", y = "Total mass gained (ln)")

ggsave("meanplot.png", plot = meanplot, width = 8, height = 5)

meanplot
```

## P NHS v P HS

### Data manipulation - log scale

```{r}
masslong2 <- dataslim2 %>%
  gather(instar, mass, ln.hatch, ln.3rd, ln.4th, ln.5th, ln.5th.2, ln.5th.3, ln.6th, ln.6th.2, ln.6th.3, ln.7th,
         ln.7th.2, ln.7th.3, ln.coc)
masslong2$instar <- gsub("ln.", "", masslong2$instar)

agelong2 <- dataslim2 %>%
  gather(instar, age, tthatch, tt3rd, tt4th, tt5th, tt5th.2, tt5th.3, tt6th, tt6th.2, tt6th.3, tt7th, tt7th.2,
         tt7th.3, ttcoc)
agelong2$instar <- gsub("tt", "", agelong2$instar)

masslong2 <- masslong2 %>% 
  select(ID, treatment, food, instar, mass)
agelong2 <- agelong2 %>% 
  select(ID, treatment, food, instar, age)

datalong2<-merge(masslong2, agelong2, by=c("ID", "treatment", "food", "instar"))

#datalong2$instar <- factor(datalong2$instar, levels = c("hatch", "3rd", "4th", "5th", "w"))

datalong2$newtreatment <- paste(datalong2$treatment, datalong2$food)
datalong2$newtreatment <- factor(datalong2$newtreatment, levels = c("P NHS DC", "P NHS TB", "P HS DC", "P HS TB"))
```

### Individual trajectories - log scale

```{r}
spaghettiplot <- ggplot(datalong2, aes(x = age, y = mass, group = ID, color = newtreatment, 
                                     shape= newtreatment)) + 
  theme_bw() + 
  geom_point() + 
  geom_line(aes(linetype = newtreatment), size = .8) + 
  #geom_errorbar(aes(ymin = mass-(ci/2), ymax = mass + (ci/2)),
               # width = .3, size = 1) + 
  #geom_errorbarh(aes(xmin = age - (age.ci/2), xmax = age + (age.ci/2)),
               #  height = .3, size = 1) + 
  scale_color_manual(values = c("#D81B60","#1E88E5", "#D81B60","#1E88E5" )) +
  scale_shape_manual(values = c(1, 1, 2, 2)) + 
  scale_linetype_manual(values = c("solid", "solid", "dashed", "dashed")) + 
  labs(x = "Total developmental age (days)", y = "Total mass gained (ln)")

spaghettiplot

ggsave("~/Desktop/lnspaghettiplot.png", plot = spaghettiplot, width = 8, height = 5)
```

### Data manipulation - normal scale

```{r}
dataslim3 <- data[data$treatment == "P NHS" | data$treatment == "P HS", ] %>%
  select(ID, food, fate, treatment, tthatch, mass.hatch, tt3rd, mass.3rd, tt4th, mass.4th, tt5th, mass.5th, tt5th.2, 
         mass.5th.2, tt5th.3, mass.5th.3, tt6th, mass.6th, tt6th.2, mass.6th.2, tt6th.3, mass.6th.3, tt7th, mass.7th, 
         tt7th.2, mass.7th.2, tt7th.3, mass.7th.3, ttcoc, mass.remove )

dataslim3$mass.coc <- dataslim3$mass.remove

masslong3 <- dataslim3 %>%
  gather(instar, mass, mass.hatch, mass.3rd, mass.4th, mass.5th, mass.5th.2, mass.5th.3, mass.6th, mass.6th.2,
         mass.6th.3, mass.7th, mass.7th.2, mass.7th.3, mass.coc)
masslong3$instar <- gsub("mass.", "", masslong3$instar)

agelong3 <- dataslim3 %>%
  gather(instar, age, tthatch, tt3rd, tt4th, tt5th, tt5th.2, tt5th.3, tt6th, tt6th.2, tt6th.3, tt7th, tt7th.2,
         tt7th.3, ttcoc)
agelong3$instar <- gsub("tt", "", agelong2$instar)

masslong3 <- masslong3 %>% 
  select(ID, treatment, food, instar, mass)
agelong3 <- agelong3 %>% 
  select(ID, treatment, food, instar, age)

datalong3<-merge(masslong3, agelong3, by=c("ID", "treatment", "food", "instar"))

#datalong2$instar <- factor(datalong2$instar, levels = c("hatch", "3rd", "4th", "5th", "w"))

datalong3$newtreatment <- paste(datalong3$treatment, datalong3$food)
datalong3$newtreatment <- factor(datalong3$newtreatment, levels = c("P NHS DC", "P NHS TB", "P HS DC", "P HS TB"))
```

### Graphing - normal scale

```{r}
spaghettiplot2 <- ggplot(datalong3, aes(x = age, y = mass, group = ID, color = newtreatment, 
                                     shape= newtreatment)) + 
  theme_bw() + 
  geom_point() + 
  ylim(0, 20000) + 
  geom_line(aes(linetype = newtreatment), size = .8) + 
  #geom_errorbar(aes(ymin = mass-(ci/2), ymax = mass + (ci/2)),
               # width = .3, size = 1) + 
  #geom_errorbarh(aes(xmin = age - (age.ci/2), xmax = age + (age.ci/2)),
               #  height = .3, size = 1) + 
  scale_color_manual(values = c("#D81B60","#1E88E5", "#D81B60","#1E88E5" )) +
  scale_shape_manual(values = c(1, 1, 2, 2)) + 
  scale_linetype_manual(values = c("solid", "solid", "dashed", "dashed")) + 
  labs(x = "Total developmental age (days)", y = "Total mass gained (mg)")

spaghettiplot2

ggsave("~/Desktop/spaghettiplot.png", plot = spaghettiplot2, width = 8, height = 5)
```

# Wasp emergence

We need to make sure the numbers of wasps emerging and eclosing from TB PNHS and DC PNHS caterpillars is the same with this data.

## Manipulate the data

```{r}
datawasp <- data %>%
  select(ID, food, treatment, date.coc, mass.remove, wet, num.w.coc, num.w.larvae, num.w.eclos)

datawasp <- datawasp[complete.cases(datawasp$num.w.coc), ]
```

```{r}
datawasp$num.w.tot <- datawasp$num.w.coc + datawasp$num.w.larvae
datawasp$prop.eclos <- datawasp$num.w.eclos / datawasp$num.w.tot
```

## Start graphing and running stats

```{r}
ggplot(data = datawasp, aes(x = treatment, y = num.w.tot)) + 
  theme_bw() + 
  geom_boxplot()
```

```{r}
ggplot(data = datawasp, aes(x = food, y = num.w.tot)) + 
  theme_bw() + 
  geom_boxplot() + 
  labs(x = "Food Type", y = "Total number of wasps emerged")
```

```{r}
waspmod1 <- lm(num.w.tot ~ food, data = datawasp[datawasp$treatment == "P NHS", ])

anova(waspmod1)
```

```{r}
ggplot(data = datawasp[datawasp$treatment == "P NHS", ], aes(x = food, y = prop.eclos)) + 
  theme_bw() + 
  geom_boxplot() + 
  labs(x = "Food Type", y = "Proportion of emerged wasps successfully eclosed")
```

```{r}
waspmod2 <- glm(prop.eclos ~ food, family = "binomial", data = datawasp[datawasp$treatment == "P NHS", ])

summary(waspmod2)
```

```{r}
ggplot(data = datawasp, aes(x = mass.remove, y = num.w.tot, color = food)) + 
  theme_bw() + 
  geom_point()
```

# Redone development time plot - means and SDs

```{r}
data$day.max <- loop(start.date = "07/12/2020", date.list = data$date.max)
data$ttmax <- data$day.max - data$day.hatch
```

```{r}
datalong4 <- data %>%
  select(ID, food, treatment, mass.max, ttmax)

meantime <- summarySE(datalong4, measurevar = "ttmax", groupvars = c("food", "treatment"), na.rm = TRUE)

meanmass <- summarySE(datalong4, measurevar = "mass.max", groupvars = c("food", "treatment"), na.rm = TRUE)

datameans <- meantime %>%
  select(food, treatment, ttmax, sd)

datameans$mass.max <- meanmass$mass.max
datameans$sdmass <- meanmass$sd
```

```{r}
meansbytrt <- ggplot(aes(x = ttmax, y = mass.max, color = food, shape = treatment), data = datalong4) +
  theme_bw() + 
  xlim(15, 45) + 
  geom_point(alpha = 0.4) + 
  scale_shape_manual(values = c(19, 1, 17, 2)) + 
  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (g)", 
       shape = "Treatment", color = "Hostplant Consumed") + 
  geom_point(data = datameans, aes(x = ttmax, y = mass.max, color = food, shape = treatment), size = 4) + 
  geom_errorbar(data = datameans, aes(ymin = mass.max - sdmass, ymax = mass.max + sdmass), size = .5) + 
  geom_errorbarh(data = datameans, aes(xmin = ttmax - sd, xmax = ttmax + sd), size = .5) + 
  guides(size = FALSE)

meansbytrt

ggsave("~/Desktop/meansbytrt.png", plot = meansbytrt, width = 8, height = 5)
```

## Add points onto developmental outcomes graph

```{r}
datalong5 <- data %>%
  select(ID, food, fate, mass.max, ttmax, area)

meantime2 <- summarySE(datalong5, measurevar = "ttmax", groupvars = c("food", "fate"), na.rm = TRUE)

meanmass2 <- summarySE(datalong5, measurevar = "mass.max", groupvars = c("food", "fate"), na.rm = TRUE)
```

### Group them into one dataframe

```{r}
datameans2 <- meantime2 %>%
  select(food, fate, ttmax, se)

datameans2$mass.max <- meanmass2$mass.max
datameans2$semass <- meanmass2$se

```

## Graphs with means only

### Maximum mass gained and age at that point

### 2022-01-01 ArchivedCode/MsCcHSFeedOutlineDec8.Rmd
Uploaded past scripts from the outline

--- 2022-01-01 ArchivedCode/MsCcHSFeedOutlineDec1.Rmd
@@
 library(Rmisc)
+library(lubridate)
+library(lmerTest)
 ```
@@
 data$treatment <- factor(data$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
+data$fate <- factor(data$fate, levels = c("wander", "em", "wowe", "wowe mongo"))
 dataviolin <- data
 dataviolin$fate <- gsub(" mongo", "", dataviolin$fate)
+dataviolin$fate <- factor(dataviolin$fate, levels = c("wander", "em", "wowe"))
 
@@
   scale_color_manual(values = c("#1E88E5", "lime green", "#D81B60"), 
-                     labels = c("WE", "Wander", "WOWE"))
+                     labels = c("Wander", "WE", "WOWE"))
 
@@
 data$treatment <- factor(data$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
+datadead$fate <- factor(datadead$fate, levels = c("dead", "wander", "em", "wowe", "wowe mongo"))
 ```
@@
   scale_fill_manual(values = c("purple", "#1E88E5", "lime green", "orange", "#D81B60"),
-                    labels = c("Died", "WE", "Wander", "WOWE", "WOWE mongo"))
+                    labels = c("Died", "Wander", "WE", "WOWE", "WOWE mongo"))
 
@@
 
+## Manipulate the data
 ```{r}
-newmeans <- ggplot(data = datalong5, aes(x = ttmax, y = mass.max, color = fate, shape = food)) + 
-  theme_bw() + 
-  xlim(15, 45) +
-  geom_point(alpha = 0.4) + 
-  scale_shape_manual(values = c(1, 19)) + 
-  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
-                     labels = c("WE", "Wander", "WOWE", "WOWE mongo")) + 
-  geom_point(aes(x = ttmax, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
-  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
-  geom_errorbarh(data = datameans2, aes(xmin = ttmax - se, xmax = ttmax + se), size = .5) + 
-  guides(size = FALSE) + 
-  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (mg)", 
-       shape = "Hostplant Consumed", color = "Developmental Outcome")
+# Internal process of the loop to convert days to dates
+expt_day <- function(start.date, date){
+  date <- mdy(date)
+  start <- mdy(start.date)
+  diff <- yday(date) - yday(start)
 
-newmeans
+  return(diff)
+}
 
-ggsave("~/Desktop/newmeans.png", newmeans, width = 8, height = 5)
-```
-
-## Stats
-
-### Maximum age differences across treatment and outcome
-
-```{r}
-maxage <- lmer(ttmax ~ fate*food + (1|bin), data = data)
-
-anova(maxage)
+# Code for the loop itself
+loop <- function(start.date, date.list){
+  days <- rep(NA, length(date.list))
+  for (i in 1:(length(days))){
+    days[i] <- expt_day(start.date = start.date, date = date.list[i])
+  }
+  return(days)
+}
 ```
@@
 ```{r}
-maxage2 <- lmer(ttmax ~ fate + food + (1|bin), data = data)
-
-anova(maxage2)
+data$day.hatch <- loop(start.date = "07/12/2020", date.list = data$date.hatch)
+data$day.max <- loop(start.date = "07/12/2020", date.list = data$date.max)
+data$ttmax <- data$day.max - data$day.hatch
 ```
-
-```{r}
-AIC(maxage, maxage2)
-```
-
-### Maximum mass
-
-```{r}
-maxmass <- lmer(mass.max ~ fate*food + (1|bin), data = data)
-
-anova(maxmass)
-```
-
-# Fig 5: Leaf matter consumed vs. max mass
 
@@
 ```{r}
+newmeans <- ggplot(data = datalong5, aes(x = ttmax, y = mass.max, color = fate, shape = food)) + 
+  theme_bw() + 
+  xlim(15, 45) +
+  geom_point(alpha = 0.4) + 
+  scale_shape_manual(values = c(1, 19)) + 
+  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
+                     labels = c("Wander", "WE", "WOWE", "WOWE mongo")) + 
+  geom_point(aes(x = ttmax, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
+  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
+  geom_errorbarh(data = datameans2, aes(xmin = ttmax - se, xmax = ttmax + se), size = .5) + 
+  guides(size = FALSE) + 
+  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (mg)", 
+       shape = "Hostplant Consumed", color = "Developmental Outcome")
+
+newmeans
+
+ggsave("~/Desktop/newmeans.png", newmeans, width = 8, height = 5)
+```
+
+## Stats
+
+### Maximum age differences across treatment and outcome
+
+```{r}
+maxage <- lmer(ttmax ~ fate*food + (1|bin), data = data)
+
+anova(maxage)
+```
+
+```{r}
+maxage2 <- lmer(ttmax ~ para*HS*food + (1|bin), data = data)
+
+anova(maxage2)
+```
+
+```{r}
+AIC(maxage, maxage2)
+```
+
+### Maximum mass
+
+```{r}
+maxmass <- lmer(mass.max ~ fate*food + (1|bin), data = data)
+
+anova(maxmass)
+```
+
+```{r}
+maxmass2 <- lmer(mass.max ~ para*HS*food + (1|bin), data = data)
+
+anova(maxmass2)
+```
+
+```{r}
+AIC(maxmass, maxmass2)
+```
+
+# Fig 5: Leaf matter consumed vs. max mass
+
+```{r}
 newarea <- ggplot(data = datalong5, aes(x = area, y = mass.max, color = fate, shape = food)) + 
@@
   scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
-                     labels = c("WE", "Wander", "WOWE", "WOWE mongo")) + 
+                     labels = c("Wander", "WE", "WOWE", "WOWE mongo")) + 
   ylim(0, 20000) + 
@@
 
+```{r}
+areatrt2 <- lmer(area ~ para*HS*food + (1|bin), data = data)
+
+anova(areatrt2)
+```
+
+```{r}
+AIC(areatrt, areatrt2)
+```
+
+```{r}
+anova(areatrt, areatrt2)
+```
+
 # Growth trajectories of different treatment groups
+
 ## Manipulate the data

### 2022-01-01 ArchivedCode/MsCcHSFeedOutlineNov10.Rmd
Uploaded past scripts from the outline

--- 2022-01-01 ArchivedCode/MsCcHSFeedOutlineDec1.Rmd
@@
 ---
-title: "MsCcHSFeed Outline"
+title: "Samples Sizes - MsCcHSFeed"
 output: html_notebook
@@
 
+## Manipulate data into correct forms
+
 ```{r}
@@
 data <- data[complete.cases(data[, 1]), ]
+```
 
+## Count stuff
+
+```{r}
+count(data[data$food == "TB" & data$para == "yes" & data$HS == "yes", ])
+count(data[data$food == "TB" & data$para == "yes" & data$HS == "no", ])
+count(data[data$food == "TB" & data$para == "no" & data$HS == "yes", ])
+count(data[data$food == "TB" & data$para == "no" & data$HS == "no", ])
 ```
+
+```{r}
+count(data[data$food == "DC" & data$para == "yes" & data$HS == "yes", ])
+count(data[data$food == "DC" & data$para == "yes" & data$HS == "no", ])
+count(data[data$food == "DC" & data$para == "no" & data$HS == "yes", ])
+count(data[data$food == "DC" & data$para == "no" & data$HS == "no", ])
+```
+
+## Make graph of outcomes
+
+```{r}
+data$treatment <- factor(data$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
+```
+
+```{r}
+bars <- ggplot(data = data, aes(x = treatment, fill = fate)) + 
+  theme_bw() + 
+  geom_bar(position = "fill") + 
+  labs(x = "Treatment group", y = "Proportion of indiviudals", fill = "Developmental Outcome")
+
+bars
+```
+
+```{r}
+bars2 <- ggplot(data = data, aes(x = treatment, fill = fate)) + 
+  theme_bw() + 
+  geom_bar(position = "stack") + 
+  facet_wrap(~food) + 
+  labs(x = "Treatment group", y = "Number of indiviudals", fill = "Developmental Outcome")
+
+bars2
+
+ggsave("~/Desktop/outcomes.png", plot = bars2, width = 8, height = 5)
+```
+
+## This time, keep the dead
 
@@
 
-# Fig 1: Counts
-
-```{r}
-count(datadead[datadead$food == "TB" & datadead$para == "yes" & datadead$HS == "yes", ])
-count(datadead[datadead$food == "TB" & datadead$para == "yes" & datadead$HS == "no", ])
-count(datadead[datadead$food == "TB" & datadead$para == "no" & datadead$HS == "yes", ])
-count(datadead[datadead$food == "TB" & datadead$para == "no" & datadead$HS == "no", ])
-```
-
-```{r}
-count(datadead[datadead$food == "DC" & datadead$para == "yes" & datadead$HS == "yes", ])
-count(datadead[datadead$food == "DC" & datadead$para == "yes" & datadead$HS == "no", ])
-count(datadead[datadead$food == "DC" & datadead$para == "no" & datadead$HS == "yes", ])
-count(datadead[datadead$food == "DC" & datadead$para == "no" & datadead$HS == "no", ])
-```
-
-# Fig 2: Violin plots of max mass
-
-```{r}
-data$treatment <- factor(data$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
-dataviolin <- data
-dataviolin$fate <- gsub(" mongo", "", dataviolin$fate)
-
-violins <- ggplot(data = dataviolin, aes(x = treatment, y = mass.max)) + 
-  geom_violin(fill = "light grey", color = "light grey") + 
-  geom_jitter(aes(color = fate), width = 0.1, height = 0) + 
-  theme_bw() + 
-  labs(x = "Treatment Group", y  = "Maximum mass achieved (mg)",  color = "Developmental Outcome") + 
-  scale_color_manual(values = c("#1E88E5", "lime green", "#D81B60"), 
-                     labels = c("WE", "Wander", "WOWE"))
-
-violins
-
-ggsave("~/Desktop/violins2.png", violins, width = 8, height = 5)
-
-```
-
-# Fig 3: Developmental outcome proportions
-
-## Make graph of outcomes
-
-```{r}
-data$treatment <- factor(data$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
-```
-
-## This time, keep the dead
-
 ```{r}
@@
   facet_wrap(~food) + 
-  labs(x = "Treatment group", y = "Proportion of indiviudals", fill = "Developmental Outcome") + 
-  scale_fill_manual(values = c("purple", "#1E88E5", "lime green", "orange", "#D81B60"),
-                    labels = c("Died", "WE", "Wander", "WOWE", "WOWE mongo"))
+  labs(x = "Treatment group", y = "Number of indiviudals", fill = "Developmental Outcome") + 
+  scale_fill_manual(values = c("#D81B60", "orange", "lime green", "#1E88E5", "purple"))
 
@@
 
-# Fig 4: Maximum mass and age
+# Growth trajectories of NP NHS vs NP HS
 
-```{r}
-newmeans <- ggplot(data = datalong5, aes(x = ttmax, y = mass.max, color = fate, shape = food)) + 
-  theme_bw() + 
-  xlim(15, 45) +
-  geom_point(alpha = 0.4) + 
-  scale_shape_manual(values = c(1, 19)) + 
-  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
-                     labels = c("WE", "Wander", "WOWE", "WOWE mongo")) + 
-  geom_point(aes(x = ttmax, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
-  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
-  geom_errorbarh(data = datameans2, aes(xmin = ttmax - se, xmax = ttmax + se), size = .5) + 
-  guides(size = FALSE) + 
-  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (mg)", 
-       shape = "Hostplant Consumed", color = "Developmental Outcome")
+## Manipulate the data
 
-newmeans
-
-ggsave("~/Desktop/newmeans.png", newmeans, width = 8, height = 5)
-```
-
-## Stats
-
-### Maximum age differences across treatment and outcome
-
-```{r}
-maxage <- lmer(ttmax ~ fate*food + (1|bin), data = data)
-
-anova(maxage)
-```
-
-```{r}
-maxage2 <- lmer(ttmax ~ fate + food + (1|bin), data = data)
-
-anova(maxage2)
-```
-
-```{r}
-AIC(maxage, maxage2)
-```
-
-### Maximum mass
-
-```{r}
-maxmass <- lmer(mass.max ~ fate*food + (1|bin), data = data)
-
-anova(maxmass)
-```
-
-# Fig 5: Leaf matter consumed vs. max mass
-
-```{r}
-#1
-scan$comb <- paste(scan$Caterpillar.ID, "_", scan$Leaf.ID)
-
-#0
-unique <- unique(scan$comb)
-consumed <- as.data.frame(unique)
-consumed$area <- 0
-
-#2-4
-for (i in 1:length(consumed$unique)){
-    subset <- filter(scan, scan$comb == consumed[i, 1])
-    value <- max(subset$Leaf.Area) - min(subset$Leaf.Area)
-    consumed[i, 2] <- value
-}
-
-#5
-consumed <- consumed %>%
-  separate(unique, c("catID", "leafID"), "_")
-
-#6
-ID <- unique(consumed$catID)
-consumedsum <- as.data.frame(ID)
-consumedsum$totalarea <- 0
-
-#7
-for (i in 1:length(consumedsum$ID)){
-  subset2 <- filter(consumed, consumed$catID == consumedsum[i, 1])
-  value2 <- sum(subset2$area)
-  consumedsum[i, 2] <- value2
-}
-
-#8
-consumedsum$ID <- as.numeric(consumedsum$ID)
-
-consumedsum <- consumedsum[consumedsum$ID %in% data$ID, ]
-
-data <- data[data$ID %in% consumedsum$ID, ]
-
-consumedsum <- consumedsum[order(consumedsum$ID), ]
-
-data$area <- consumedsum$totalarea
-
-```
-
-```{r}
-datalong5 <- data %>%
-  select(ID, food, fate, mass.max, ttmax, area)
-
-meantime2 <- summarySE(datalong5, measurevar = "ttmax", groupvars = c("food", "fate"), na.rm = TRUE)
-
-meanmass2 <- summarySE(datalong5, measurevar = "mass.max", groupvars = c("food", "fate"), na.rm = TRUE)
-
-meanarea2 <- summarySE(datalong5, measurevar = "area", groupvars = c("food", "fate"), na.rm = TRUE)
-```
-
-### Group them into one dataframe
-
-```{r}
-datameans2 <- meantime2 %>%
-  select(food, fate, ttmax, se)
-
-datameans2$mass.max <- meanmass2$mass.max
-datameans2$semass <- meanmass2$se
-datameans2$area <- meanarea2$area
-datameans2$arease <- meanarea2$se
-
-```
-
-```{r}
-newarea <- ggplot(data = datalong5, aes(x = area, y = mass.max, color = fate, shape = food)) + 
-  theme_bw() + 
-  geom_point(alpha = 0.4) + 
-  scale_shape_manual(values = c(1, 19)) + 
-  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
-                     labels = c("WE", "Wander", "WOWE", "WOWE mongo")) + 
-  ylim(0, 20000) + 
-  xlim(0, 6000) +
-  geom_point(aes(x = area, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
-  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
-  geom_errorbarh(data = datameans2, aes(xmin = area - arease, xmax = area + arease), size = .5) + 
-  guides(size = FALSE) + 
-  labs(x = "Hostplant leaf area consumed (cm^2)", y = "Maximum mass achieved (mg)", 
-       shape = "Hostplant Consumed", color = "Developmental Outcome")
-
-newarea
-
-ggsave("~/Desktop/newarea.png", newarea, width = 8, height = 5)
-```
-
-## Stats
-
-```{r}
-areatrt <- lmer(area ~ fate*food + (1|bin), data = data)
-
-anova(areatrt)
-```
-
-# Growth trajectories of different treatment groups 
-## Manipulate the data
 ```{r}
@@
 
-data$day.5th.2 <- loop(start.date = "07/12/2020", date.list = data$date.5th.2)
-data$day.5th.3 <- loop(start.date = "07/12/2020", date.list = data$date.5th.3)
-data$day.6th <- loop(start.date = "07/12/2020", date.list = data$date.6th)
-data$day.6th.2 <- loop(start.date = "07/12/2020", date.list = data$date.6th.2)
-data$day.6th.3 <- loop(start.date = "07/12/2020", date.list = data$date.6th.3)
-data$day.7th <- loop(start.date = "07/12/2020", date.list = data$date.7th)
-data$day.7th.2 <- loop(start.date = "07/12/2020", date.list = data$date.7th.2)
-data$day.7th.3 <- loop(start.date = "07/12/2020", date.list = data$date.7th.3)
-data$day.coc <- loop(start.date = "07/12/2020", date.list = data$date.coc)
-
 data$tthatch <- 0
@@
 data$ttw <- data$day.w - data$day.hatch
-
-data$tt5th.2 <- data$day.5th.2 - data$day.hatch
-data$tt5th.3 <- data$day.5th.3 - data$day.hatch
-data$tt6th <- data$day.6th - data$day.hatch
-data$tt6th.2 <- data$day.6th.2 - data$day.hatch
-data$tt6th.3 <- data$day.6th.3 - data$day.hatch
-data$tt7th <- data$day.7th - data$day.hatch
-data$tt7th.2 <- data$day.7th.2 - data$day.hatch
-data$tt7th.3 <- data$day.7th.3 - data$day.hatch
-data$ttcoc <- data$day.coc - data$day.hatch
-
 ```
@@
 data$ln.w <- log(data$mass.w)
-
-data$ln.5th.2 <- log(data$mass.5th.2)
-data$ln.5th.3 <- log(data$mass.5th.3)
-data$ln.6th <- log(data$mass.6th)
-data$ln.6th.2 <- log(data$mass.6th.2)
-data$ln.6th.3 <- log(data$mass.6th.3)
-data$ln.7th <- log(data$mass.7th)
-data$ln.7th.2 <- log(data$mass.7th.2)
-data$ln.7th.3 <- log(data$mass.7th.3)
-data$ln.coc <- log(data$mass.remove)
-
 ```
@@
 
-dataslim2 <- data[data$treatment == "P NHS" | data$treatment == "P HS", ] %>%
-  select(ID, food, fate, treatment, tthatch, ln.hatch, tt3rd, ln.3rd, tt4th, ln.4th, tt5th, ln.5th, tt5th.2, 
-         ln.5th.2, tt5th.3, ln.5th.3, tt6th, ln.6th, tt6th.2, ln.6th.2, tt6th.3, ln.6th.3, tt7th, ln.7th, 
-         tt7th.2, ln.7th.2, tt7th.3, ln.7th.3, ttcoc, ln.coc )
 ```
-
-## NP NHS vs NP HS
-
-### More manupulation
 
@@
 
-### Plot the data (with CIs)
+## Plot the data (with CIs)
 
@@
 ```
-
-## P NHS v P HS
-
-### Data manipulation - log scale
-
-```{r}
-masslong2 <- dataslim2 %>%
-  gather(instar, mass, ln.hatch, ln.3rd, ln.4th, ln.5th, ln.5th.2, ln.5th.3, ln.6th, ln.6th.2, ln.6th.3, ln.7th,
-         ln.7th.2, ln.7th.3, ln.coc)
-masslong2$instar <- gsub("ln.", "", masslong2$instar)
-
-agelong2 <- dataslim2 %>%
-  gather(instar, age, tthatch, tt3rd, tt4th, tt5th, tt5th.2, tt5th.3, tt6th, tt6th.2, tt6th.3, tt7th, tt7th.2,
-         tt7th.3, ttcoc)
-agelong2$instar <- gsub("tt", "", agelong2$instar)
-
-masslong2 <- masslong2 %>% 
-  select(ID, treatment, food, instar, mass)
-agelong2 <- agelong2 %>% 
-  select(ID, treatment, food, instar, age)
-
-datalong2<-merge(masslong2, agelong2, by=c("ID", "treatment", "food", "instar"))
-
-#datalong2$instar <- factor(datalong2$instar, levels = c("hatch", "3rd", "4th", "5th", "w"))
-
-datalong2$newtreatment <- paste(datalong2$treatment, datalong2$food)
-datalong2$newtreatment <- factor(datalong2$newtreatment, levels = c("P NHS DC", "P NHS TB", "P HS DC", "P HS TB"))
-```
-
-### Individual trajectories - log scale
-
-```{r}
-spaghettiplot <- ggplot(datalong2, aes(x = age, y = mass, group = ID, color = newtreatment, 
-                                     shape= newtreatment)) + 
-  theme_bw() + 
-  geom_point() + 
-  geom_line(aes(linetype = newtreatment), size = .8) + 
-  #geom_errorbar(aes(ymin = mass-(ci/2), ymax = mass + (ci/2)),
-               # width = .3, size = 1) + 
-  #geom_errorbarh(aes(xmin = age - (age.ci/2), xmax = age + (age.ci/2)),
-               #  height = .3, size = 1) + 
-  scale_color_manual(values = c("#D81B60","#1E88E5", "#D81B60","#1E88E5" )) +
-  scale_shape_manual(values = c(1, 1, 2, 2)) + 
-  scale_linetype_manual(values = c("solid", "solid", "dashed", "dashed")) + 
-  labs(x = "Total developmental age (days)", y = "Total mass gained (ln)")
-
-spaghettiplot
-
-ggsave("~/Desktop/lnspaghettiplot.png", plot = spaghettiplot, width = 8, height = 5)
-```
-
-### Data manipulation - normal scale
-
-```{r}
-dataslim3 <- data[data$treatment == "P NHS" | data$treatment == "P HS", ] %>%
-  select(ID, food, fate, treatment, tthatch, mass.hatch, tt3rd, mass.3rd, tt4th, mass.4th, tt5th, mass.5th, tt5th.2, 
-         mass.5th.2, tt5th.3, mass.5th.3, tt6th, mass.6th, tt6th.2, mass.6th.2, tt6th.3, mass.6th.3, tt7th, mass.7th, 
-         tt7th.2, mass.7th.2, tt7th.3, mass.7th.3, ttcoc, mass.remove )
-
-dataslim3$mass.coc <- dataslim3$mass.remove
-
-masslong3 <- dataslim3 %>%
-  gather(instar, mass, mass.hatch, mass.3rd, mass.4th, mass.5th, mass.5th.2, mass.5th.3, mass.6th, mass.6th.2,
-         mass.6th.3, mass.7th, mass.7th.2, mass.7th.3, mass.coc)
-masslong3$instar <- gsub("mass.", "", masslong3$instar)
-
-agelong3 <- dataslim3 %>%
-  gather(instar, age, tthatch, tt3rd, tt4th, tt5th, tt5th.2, tt5th.3, tt6th, tt6th.2, tt6th.3, tt7th, tt7th.2,
-         tt7th.3, ttcoc)
-agelong3$instar <- gsub("tt", "", agelong2$instar)
-
-masslong3 <- masslong3 %>% 
-  select(ID, treatment, food, instar, mass)
-agelong3 <- agelong3 %>% 
-  select(ID, treatment, food, instar, age)
-
-datalong3<-merge(masslong3, agelong3, by=c("ID", "treatment", "food", "instar"))
-
-#datalong2$instar <- factor(datalong2$instar, levels = c("hatch", "3rd", "4th", "5th", "w"))
-
-datalong3$newtreatment <- paste(datalong3$treatment, datalong3$food)
-datalong3$newtreatment <- factor(datalong3$newtreatment, levels = c("P NHS DC", "P NHS TB", "P HS DC", "P HS TB"))
-```
-
-### Graphing - normal scale
-
-```{r}
-spaghettiplot2 <- ggplot(datalong3, aes(x = age, y = mass, group = ID, color = newtreatment, 
-                                     shape= newtreatment)) + 
-  theme_bw() + 
-  geom_point() + 
-  ylim(0, 20000) + 
-  geom_line(aes(linetype = newtreatment), size = .8) + 
-  #geom_errorbar(aes(ymin = mass-(ci/2), ymax = mass + (ci/2)),
-               # width = .3, size = 1) + 
-  #geom_errorbarh(aes(xmin = age - (age.ci/2), xmax = age + (age.ci/2)),
-               #  height = .3, size = 1) + 
-  scale_color_manual(values = c("#D81B60","#1E88E5", "#D81B60","#1E88E5" )) +
-  scale_shape_manual(values = c(1, 1, 2, 2)) + 
-  scale_linetype_manual(values = c("solid", "solid", "dashed", "dashed")) + 
-  labs(x = "Total developmental age (days)", y = "Total mass gained (mg)")
-
-spaghettiplot2
-
-ggsave("~/Desktop/spaghettiplot.png", plot = spaghettiplot2, width = 8, height = 5)
-```
-
-# Wasp emergence
-
-We need to make sure the numbers of wasps emerging and eclosing from TB PNHS and DC PNHS caterpillars is the same with this data.
-
-## Manipulate the data
-
-```{r}
-datawasp <- data %>%
-  select(ID, food, treatment, date.coc, mass.remove, wet, num.w.coc, num.w.larvae, num.w.eclos)
-
-datawasp <- datawasp[complete.cases(datawasp$num.w.coc), ]
-```
-
-```{r}
-datawasp$num.w.tot <- datawasp$num.w.coc + datawasp$num.w.larvae
-datawasp$prop.eclos <- datawasp$num.w.eclos / datawasp$num.w.tot
-```
-
-## Start graphing and running stats
-
-```{r}
-ggplot(data = datawasp, aes(x = treatment, y = num.w.tot)) + 
-  theme_bw() + 
-  geom_boxplot()
-```
-
-```{r}
-ggplot(data = datawasp, aes(x = food, y = num.w.tot)) + 
-  theme_bw() + 
-  geom_boxplot() + 
-  labs(x = "Food Type", y = "Total number of wasps emerged")
-```
-
-```{r}
-waspmod1 <- lm(num.w.tot ~ food, data = datawasp[datawasp$treatment == "P NHS", ])
-
-anova(waspmod1)
-```
-
-```{r}
-ggplot(data = datawasp[datawasp$treatment == "P NHS", ], aes(x = food, y = prop.eclos)) + 
-  theme_bw() + 
-  geom_boxplot() + 
-  labs(x = "Food Type", y = "Proportion of emerged wasps successfully eclosed")
-```
-
-```{r}
-waspmod2 <- glm(prop.eclos ~ food, family = "binomial", data = datawasp[datawasp$treatment == "P NHS", ])
-
-summary(waspmod2)
-```
-
-```{r}
-ggplot(data = datawasp, aes(x = mass.remove, y = num.w.tot, color = food)) + 
-  theme_bw() + 
-  geom_point()
-```
-
-# Redone development time plot - means and SDs
-
-```{r}
-data$day.max <- loop(start.date = "07/12/2020", date.list = data$date.max)
-data$ttmax <- data$day.max - data$day.hatch
-```
-
-```{r}
-datalong4 <- data %>%
-  select(ID, food, treatment, mass.max, ttmax)
-
-meantime <- summarySE(datalong4, measurevar = "ttmax", groupvars = c("food", "treatment"), na.rm = TRUE)
-
-meanmass <- summarySE(datalong4, measurevar = "mass.max", groupvars = c("food", "treatment"), na.rm = TRUE)
-
-datameans <- meantime %>%
-  select(food, treatment, ttmax, sd)
-
-datameans$mass.max <- meanmass$mass.max
-datameans$sdmass <- meanmass$sd
-```
-
-```{r}
-meansbytrt <- ggplot(aes(x = ttmax, y = mass.max, color = food, shape = treatment), data = datalong4) +
-  theme_bw() + 
-  xlim(15, 45) + 
-  geom_point(alpha = 0.4) + 
-  scale_shape_manual(values = c(19, 1, 17, 2)) + 
-  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (g)", 
-       shape = "Treatment", color = "Hostplant Consumed") + 
-  geom_point(data = datameans, aes(x = ttmax, y = mass.max, color = food, shape = treatment), size = 4) + 
-  geom_errorbar(data = datameans, aes(ymin = mass.max - sdmass, ymax = mass.max + sdmass), size = .5) + 
-  geom_errorbarh(data = datameans, aes(xmin = ttmax - sd, xmax = ttmax + sd), size = .5) + 
-  guides(size = FALSE)
-
-meansbytrt
-
-ggsave("~/Desktop/meansbytrt.png", plot = meansbytrt, width = 8, height = 5)
-```
-
-## Add points onto developmental outcomes graph
-
-```{r}
-datalong5 <- data %>%
-  select(ID, food, fate, mass.max, ttmax, area)
-
-meantime2 <- summarySE(datalong5, measurevar = "ttmax", groupvars = c("food", "fate"), na.rm = TRUE)
-
-meanmass2 <- summarySE(datalong5, measurevar = "mass.max", groupvars = c("food", "fate"), na.rm = TRUE)
-```
-
-### Group them into one dataframe
-
-```{r}
-datameans2 <- meantime2 %>%
-  select(food, fate, ttmax, se)
-
-datameans2$mass.max <- meanmass2$mass.max
-datameans2$semass <- meanmass2$se
-
-```
-
-## Graphs with means only
-
-### Maximum mass gained and age at that point

### 2022-01-01 ArchivedCode/MsCcHSFeedOutlineNov15.Rmd
Uploaded past scripts from the outline

--- 2022-01-01 ArchivedCode/MsCcHSFeedOutlineDec1.Rmd
@@
 data <- data[complete.cases(data[, 1]), ]
+```
 
+# Count stuff
+
+```{r}
+count(data[data$food == "TB" & data$para == "yes" & data$HS == "yes", ])
+count(data[data$food == "TB" & data$para == "yes" & data$HS == "no", ])
+count(data[data$food == "TB" & data$para == "no" & data$HS == "yes", ])
+count(data[data$food == "TB" & data$para == "no" & data$HS == "no", ])
 ```
+
+```{r}
+count(data[data$food == "DC" & data$para == "yes" & data$HS == "yes", ])
+count(data[data$food == "DC" & data$para == "yes" & data$HS == "no", ])
+count(data[data$food == "DC" & data$para == "no" & data$HS == "yes", ])
+count(data[data$food == "DC" & data$para == "no" & data$HS == "no", ])
+```
+
+# Developmental outcome proportions
+
+## Make graph of outcomes
+
+```{r}
+data$treatment <- factor(data$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
+```
+
+```{r}
+bars <- ggplot(data = data, aes(x = treatment, fill = fate)) + 
+  theme_bw() + 
+  geom_bar(position = "fill") + 
+  labs(x = "Treatment group", y = "Proportion of indiviudals", fill = "Developmental Outcome")
+
+bars
+```
+
+```{r}
+bars2 <- ggplot(data = data, aes(x = treatment, fill = fate)) + 
+  theme_bw() + 
+  geom_bar(position = "stack") + 
+  facet_wrap(~food) + 
+  labs(x = "Treatment group", y = "Number of indiviudals", fill = "Developmental Outcome")
+
+bars2
+
+ggsave("~/Desktop/outcomes.png", plot = bars2, width = 8, height = 5)
+```
+
+## This time, keep the dead
 
@@
   labs(x = "Treatment group", y = "Proportion of indiviudals", fill = "Developmental Outcome") + 
-  scale_fill_manual(values = c("purple", "#1E88E5", "lime green", "orange", "#D81B60"),
-                    labels = c("Died", "WE", "Wander", "WOWE", "WOWE mongo"))
+  scale_fill_manual(values = c("#D81B60", "orange", "lime green", "#1E88E5", "purple"))
 
@@
 
-# Fig 4: Maximum mass and age
+# Growth trajectories of different treatment groups
 
-```{r}
-newmeans <- ggplot(data = datalong5, aes(x = ttmax, y = mass.max, color = fate, shape = food)) + 
-  theme_bw() + 
-  xlim(15, 45) +
-  geom_point(alpha = 0.4) + 
-  scale_shape_manual(values = c(1, 19)) + 
-  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
-                     labels = c("WE", "Wander", "WOWE", "WOWE mongo")) + 
-  geom_point(aes(x = ttmax, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
-  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
-  geom_errorbarh(data = datameans2, aes(xmin = ttmax - se, xmax = ttmax + se), size = .5) + 
-  guides(size = FALSE) + 
-  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (mg)", 
-       shape = "Hostplant Consumed", color = "Developmental Outcome")
+### Manipulate the data
 
-newmeans
-
-ggsave("~/Desktop/newmeans.png", newmeans, width = 8, height = 5)
-```
-
-## Stats
-
-### Maximum age differences across treatment and outcome
-
-```{r}
-maxage <- lmer(ttmax ~ fate*food + (1|bin), data = data)
-
-anova(maxage)
-```
-
-```{r}
-maxage2 <- lmer(ttmax ~ fate + food + (1|bin), data = data)
-
-anova(maxage2)
-```
-
-```{r}
-AIC(maxage, maxage2)
-```
-
-### Maximum mass
-
-```{r}
-maxmass <- lmer(mass.max ~ fate*food + (1|bin), data = data)
-
-anova(maxmass)
-```
-
-# Fig 5: Leaf matter consumed vs. max mass
-
-```{r}
-#1
-scan$comb <- paste(scan$Caterpillar.ID, "_", scan$Leaf.ID)
-
-#0
-unique <- unique(scan$comb)
-consumed <- as.data.frame(unique)
-consumed$area <- 0
-
-#2-4
-for (i in 1:length(consumed$unique)){
-    subset <- filter(scan, scan$comb == consumed[i, 1])
-    value <- max(subset$Leaf.Area) - min(subset$Leaf.Area)
-    consumed[i, 2] <- value
-}
-
-#5
-consumed <- consumed %>%
-  separate(unique, c("catID", "leafID"), "_")
-
-#6
-ID <- unique(consumed$catID)
-consumedsum <- as.data.frame(ID)
-consumedsum$totalarea <- 0
-
-#7
-for (i in 1:length(consumedsum$ID)){
-  subset2 <- filter(consumed, consumed$catID == consumedsum[i, 1])
-  value2 <- sum(subset2$area)
-  consumedsum[i, 2] <- value2
-}
-
-#8
-consumedsum$ID <- as.numeric(consumedsum$ID)
-
-consumedsum <- consumedsum[consumedsum$ID %in% data$ID, ]
-
-data <- data[data$ID %in% consumedsum$ID, ]
-
-consumedsum <- consumedsum[order(consumedsum$ID), ]
-
-data$area <- consumedsum$totalarea
-
-```
-
-```{r}
-datalong5 <- data %>%
-  select(ID, food, fate, mass.max, ttmax, area)
-
-meantime2 <- summarySE(datalong5, measurevar = "ttmax", groupvars = c("food", "fate"), na.rm = TRUE)
-
-meanmass2 <- summarySE(datalong5, measurevar = "mass.max", groupvars = c("food", "fate"), na.rm = TRUE)
-
-meanarea2 <- summarySE(datalong5, measurevar = "area", groupvars = c("food", "fate"), na.rm = TRUE)
-```
-
-### Group them into one dataframe
-
-```{r}
-datameans2 <- meantime2 %>%
-  select(food, fate, ttmax, se)
-
-datameans2$mass.max <- meanmass2$mass.max
-datameans2$semass <- meanmass2$se
-datameans2$area <- meanarea2$area
-datameans2$arease <- meanarea2$se
-
-```
-
-```{r}
-newarea <- ggplot(data = datalong5, aes(x = area, y = mass.max, color = fate, shape = food)) + 
-  theme_bw() + 
-  geom_point(alpha = 0.4) + 
-  scale_shape_manual(values = c(1, 19)) + 
-  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
-                     labels = c("WE", "Wander", "WOWE", "WOWE mongo")) + 
-  ylim(0, 20000) + 
-  xlim(0, 6000) +
-  geom_point(aes(x = area, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
-  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
-  geom_errorbarh(data = datameans2, aes(xmin = area - arease, xmax = area + arease), size = .5) + 
-  guides(size = FALSE) + 
-  labs(x = "Hostplant leaf area consumed (cm^2)", y = "Maximum mass achieved (mg)", 
-       shape = "Hostplant Consumed", color = "Developmental Outcome")
-
-newarea
-
-ggsave("~/Desktop/newarea.png", newarea, width = 8, height = 5)
-```
-
-## Stats
-
-```{r}
-areatrt <- lmer(area ~ fate*food + (1|bin), data = data)
-
-anova(areatrt)
-```
-
-# Growth trajectories of different treatment groups 
-## Manipulate the data
 ```{r}
@@
 datalong5 <- data %>%
-  select(ID, food, fate, mass.max, ttmax, area)
+  select(ID, food, fate, mass.max, ttmax)
 
@@
 ### Maximum mass gained and age at that point
+
+```{r}
+ggplot(aes(x = ttmax, y = mass.max, color = food, shape = fate), 
+       data = datameans2) + 
+  theme_bw() + 
+  xlim(15, 45) +
+  geom_point(size = 4) + 
+  scale_shape_manual(values = c(5, 2, 1, 19)) + 
+  geom_errorbar(aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
+  geom_errorbarh(aes(xmin = ttmax - se, xmax = ttmax + se), size = .5) + 
+  guides(size = FALSE) + 
+  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (g)", 
+       shape = "Developmental Outcome", color = "Hostplant Consumed") +
+  geom_point(data = datalong5, aes(x = ttmax, y = mass.max, color = food, shape = fate), alpha = 0.4)
+```

### 2022-01-01 ArchivedCode/MsCcHSFeedOutlineNov23.Rmd
Uploaded past scripts from the outline

--- 2022-01-01 ArchivedCode/MsCcHSFeedOutlineDec1.Rmd
@@
 
+# Count stuff
+
+```{r}
+count(data[data$food == "TB" & data$para == "yes" & data$HS == "yes", ])
+count(data[data$food == "TB" & data$para == "yes" & data$HS == "no", ])
+count(data[data$food == "TB" & data$para == "no" & data$HS == "yes", ])
+count(data[data$food == "TB" & data$para == "no" & data$HS == "no", ])
+```
+
+```{r}
+count(data[data$food == "DC" & data$para == "yes" & data$HS == "yes", ])
+count(data[data$food == "DC" & data$para == "yes" & data$HS == "no", ])
+count(data[data$food == "DC" & data$para == "no" & data$HS == "yes", ])
+count(data[data$food == "DC" & data$para == "no" & data$HS == "no", ])
+```
+
+# Developmental outcome proportions
+
+## Make graph of outcomes
+
+```{r}
+data$treatment <- factor(data$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
+```
+
+```{r}
+bars <- ggplot(data = data, aes(x = treatment, fill = fate)) + 
+  theme_bw() + 
+  geom_bar(position = "fill") + 
+  labs(x = "Treatment group", y = "Proportion of indiviudals", fill = "Developmental Outcome")
+
+bars
+```
+
+```{r}
+bars2 <- ggplot(data = data, aes(x = treatment, fill = fate)) + 
+  theme_bw() + 
+  geom_bar(position = "stack") + 
+  facet_wrap(~food) + 
+  labs(x = "Treatment group", y = "Number of indiviudals", fill = "Developmental Outcome")
+
+bars2
+
+ggsave("~/Desktop/outcomes.png", plot = bars2, width = 8, height = 5)
+```
+
+## This time, keep the dead
+
 ```{r}
@@
   labs(x = "Treatment group", y = "Proportion of indiviudals", fill = "Developmental Outcome") + 
-  scale_fill_manual(values = c("purple", "#1E88E5", "lime green", "orange", "#D81B60"),
-                    labels = c("Died", "WE", "Wander", "WOWE", "WOWE mongo"))
+  scale_fill_manual(values = c("purple", "#1E88E5", "lime green", "orange", "#D81B60"))
 
@@
 ### Maximum mass gained and age at that point
+
+```{r}
+newmeans <- ggplot(data = datalong5, aes(x = ttmax, y = mass.max, color = fate, shape = food)) + 
+  theme_bw() + 
+  xlim(15, 45) +
+  geom_point(alpha = 0.4) + 
+  scale_shape_manual(values = c(1, 19)) + 
+  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
+                     labels = c("WE", "Wander", "WOWE", "WOWE mongo")) + 
+  geom_point(aes(x = ttmax, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
+  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
+  geom_errorbarh(data = datameans2, aes(xmin = ttmax - se, xmax = ttmax + se), size = .5) + 
+  guides(size = FALSE) + 
+  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (mg)", 
+       shape = "Hostplant Consumed", color = "Developmental Outcome")
+
+newmeans
+
+ggsave("~/Desktop/newmeans.png", newmeans, width = 8, height = 5)
+```
+
+# Leaf matter consumed vs. max mass
+
+```{r}
+#1
+scan$comb <- paste(scan$Caterpillar.ID, "_", scan$Leaf.ID)
+
+#0
+unique <- unique(scan$comb)
+consumed <- as.data.frame(unique)
+consumed$area <- 0
+
+#2-4
+for (i in 1:length(consumed$unique)){
+    subset <- filter(scan, scan$comb == consumed[i, 1])
+    value <- max(subset$Leaf.Area) - min(subset$Leaf.Area)
+    consumed[i, 2] <- value
+}
+
+#5
+consumed <- consumed %>%
+  separate(unique, c("catID", "leafID"), "_")
+
+#6
+ID <- unique(consumed$catID)
+consumedsum <- as.data.frame(ID)
+consumedsum$totalarea <- 0
+
+#7
+for (i in 1:length(consumedsum$ID)){
+  subset2 <- filter(consumed, consumed$catID == consumedsum[i, 1])
+  value2 <- sum(subset2$area)
+  consumedsum[i, 2] <- value2
+}
+
+#8
+consumedsum$ID <- as.numeric(consumedsum$ID)
+
+consumedsum <- consumedsum[consumedsum$ID %in% data$ID, ]
+
+data <- data[data$ID %in% consumedsum$ID, ]
+
+consumedsum <- consumedsum[order(consumedsum$ID), ]
+
+data$area <- consumedsum$totalarea
+
+```
+
+```{r}
+datalong5 <- data %>%
+  select(ID, food, fate, mass.max, ttmax, area)
+
+meantime2 <- summarySE(datalong5, measurevar = "ttmax", groupvars = c("food", "fate"), na.rm = TRUE)
+
+meanmass2 <- summarySE(datalong5, measurevar = "mass.max", groupvars = c("food", "fate"), na.rm = TRUE)
+
+meanarea2 <- summarySE(datalong5, measurevar = "area", groupvars = c("food", "fate"), na.rm = TRUE)
+```
+
+### Group them into one dataframe
+
+```{r}
+datameans2 <- meantime2 %>%
+  select(food, fate, ttmax, se)
+
+datameans2$mass.max <- meanmass2$mass.max
+datameans2$semass <- meanmass2$se
+datameans2$area <- meanarea2$area
+datameans2$arease <- meanarea2$se
+
+```
+
+```{r}
+# OLD DON'T RUN
+#newarea <- ggplot(aes(x = area, y = mass.max, color = food, shape = fate), 
+       data = datameans) + 
+  theme_bw() + 
+  ylim(0, 20) + 
+  xlim(0, 6000) +
+  geom_point(size = 4) + 
+  scale_shape_manual(values = c(5, 2, 1, 19)) + 
+  geom_errorbar(aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
+  geom_errorbarh(aes(xmin = area - searea, xmax = area + searea), size = .5) + 
+  guides(size = FALSE) + 
+  labs(x = "Hostplant leaf area consumed (cm^2)", y = "Maximum mass achieved (g)", 
+       shape = "Developmental Outcome", color = "Hostplant Consumed")
+
+#newarea
+
+#ggsave("~/Desktop/newarea.png", newarea, width = 8, height = 5)
+```
+
+```{r}
+newarea <- ggplot(data = datalong5, aes(x = area, y = mass.max, color = fate, shape = food)) + 
+  theme_bw() + 
+  geom_point(alpha = 0.4) + 
+  scale_shape_manual(values = c(1, 19)) + 
+  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
+                     labels = c("WE", "Wander", "WOWE", "WOWE mongo")) + 
+  ylim(0, 20000) + 
+  xlim(0, 6000) +
+  geom_point(aes(x = area, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
+  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
+  geom_errorbarh(data = datameans2, aes(xmin = area - arease, xmax = area + arease), size = .5) + 
+  guides(size = FALSE) + 
+  labs(x = "Hostplant leaf area consumed (cm^2)", y = "Maximum mass achieved (mg)", 
+       shape = "Hostplant Consumed", color = "Developmental Outcome")
+
+newarea
+
+ggsave("~/Desktop/newarea.png", newarea, width = 8, height = 5)
+```
+
+# Violin plots of max mass
+
+```{r}
+data$treatment <- factor(data$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
+
+violins <- ggplot(data = data, aes(x = treatment, y = mass.max)) + 
+  geom_violin(fill = "light grey", color = "light grey") + 
+  geom_jitter(aes(color = fate), width = 0.1, height = 0) + 
+  theme_bw() + 
+  labs(x = "Treatment Group", y  = "Maximum mass achieved (mg)",  color = "Developmental Outcome") + 
+  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"))
+
+violins
+
+ggsave("~/Desktop/violins.png", violins, width = 8, height = 5)
+```

### 2022-01-01 ArchivedCode/MsCcHSFeedOutlineNov24Condensed.Rmd
Uploaded past scripts from the outline

--- 2022-01-01 ArchivedCode/MsCcHSFeedOutlineDec1.Rmd
@@
 
-```{r}
-datadead <- read.csv("~/Desktop/MsCcHSFeedJan1MOD.csv")
-datadead <- datadead[datadead$fate != "quink" & datadead$fate != "wander*" & datadead$fate != "?", ]
-datadead <- datadead[complete.cases(datadead[, 1]), ]
-datadead$treatment <- factor(datadead$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
-```
-
-# Fig 1: Counts
-
-```{r}
-count(datadead[datadead$food == "TB" & datadead$para == "yes" & datadead$HS == "yes", ])
-count(datadead[datadead$food == "TB" & datadead$para == "yes" & datadead$HS == "no", ])
-count(datadead[datadead$food == "TB" & datadead$para == "no" & datadead$HS == "yes", ])
-count(datadead[datadead$food == "TB" & datadead$para == "no" & datadead$HS == "no", ])
-```
-
-```{r}
-count(datadead[datadead$food == "DC" & datadead$para == "yes" & datadead$HS == "yes", ])
-count(datadead[datadead$food == "DC" & datadead$para == "yes" & datadead$HS == "no", ])
-count(datadead[datadead$food == "DC" & datadead$para == "no" & datadead$HS == "yes", ])
-count(datadead[datadead$food == "DC" & datadead$para == "no" & datadead$HS == "no", ])
-```
-
-# Fig 2: Violin plots of max mass
+# Fig 1: Violin plots of max mass
 
@@
 
-# Fig 3: Developmental outcome proportions
+# Fig 2: Developmental outcome proportions
 
@@
 ## This time, keep the dead
+
+```{r}
+datadead <- read.csv("~/Desktop/MsCcHSFeedJan1MOD.csv")
+datadead <- datadead[datadead$fate != "quink" & datadead$fate != "wander*" & datadead$fate != "?", ]
+datadead <- datadead[complete.cases(datadead[, 1]), ]
+datadead$treatment <- factor(datadead$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
+```
 
@@
 
-# Fig 4: Maximum mass and age
+# Fig 3: Maximum mass and age
 
@@
 
-# Fig 5: Leaf matter consumed vs. max mass
+# Fig 4: Leaf matter consumed vs. max mass
 
@@
 # Growth trajectories of different treatment groups
-## Manipulate the data
+
+### Manipulate the data
+
 ```{r}

### 2022-01-01 ArchivedCode/MsCcHSFeedOutlineNov5.Rmd
Uploaded past scripts from the outline

--- 2022-01-01 ArchivedCode/MsCcHSFeedOutlineNov10.Rmd
@@
   theme_bw() + 
-  geom_bar(position = "fill") + 
+  geom_bar(position = "stack") + 
   facet_wrap(~food) + 

### 2022-01-01 MsCcHSFeedOutlineDec15.Rmd
Uploaded past scripts from the outline

--- 2022-01-01 ArchivedCode/MsCcHSFeedOutlineDec8.Rmd
@@
 data <- data[complete.cases(data[, 1]), ]
+data$fate <- factor(data$fate, levels = c("wander", "em", "wowe", "wowe mongo"))
 
@@
 data$treatment <- factor(data$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
-data$fate <- factor(data$fate, levels = c("wander", "em", "wowe", "wowe mongo"))
+
 dataviolin <- data
@@
 data$ttmax <- data$day.max - data$day.hatch
+
+data$mass.max <- data$mass.max / 1000
 ```
@@
 
+data$area <- data$area / 10000
+
 ```
@@
   guides(size = FALSE) + 
-  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (mg)", 
+  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (g)", 
        shape = "Hostplant Consumed", color = "Developmental Outcome")
@@
                      labels = c("Wander", "WE", "WOWE", "WOWE mongo")) + 
-  ylim(0, 20000) + 
-  xlim(0, 6000) +
+  ylim(0, 20) + 
+  xlim(0, .6) +
   geom_point(aes(x = area, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
@@
   guides(size = FALSE) + 
-  labs(x = "Hostplant leaf area consumed (cm^2)", y = "Maximum mass achieved (mg)", 
+  labs(x = "Hostplant leaf area consumed (m^2)", y = "Maximum mass achieved (g)", 
        shape = "Hostplant Consumed", color = "Developmental Outcome")

### 2022-01-07 MsCcHSFeedOutlineDec15.Rmd
Added code for binomial comparisons of death rates and WOWE/WE rates

@@
 anova(areatrt, areatrt2)
+```
+
+# Additional analyses
+
+## Binomial of deaths between NP and P groups
+
+```{r}
+binomdeath <- datadead %>%
+  select(ID, food, para, survived)
+
+binomdeath$survived <- gsub("yes", 1, binomdeath$survived)
+binomdeath$survived <- gsub("no", 0, binomdeath$survived)
+
+binomdeath$survived <- as.numeric(binomdeath$survived)
+```
+
+### Run stats
+
+```{r}
+death <- glm(survived ~ food*para, data = binomdeath, family = "binomial")
+
+summary(death)
+```
+
+```{r}
+death2 <- glm(survived ~ para, data = binomdeath, family = "binomial")
+
+summary(death2)
+```
+
+## Binomial of WOWE mongo outcomes
+
+```{r}
+binomWOWE <- data %>%
+  select(ID, food, fate)
+
+binomWOWE$fate <- gsub("wowe mongo", 1, binomWOWE$fate)
+binomWOWE$fate <- gsub("wowe", 0, binomWOWE$fate)
+binomWOWE$fate <- gsub("em", 0, binomWOWE$fate)
+binomWOWE$fate <- gsub("wander", 0, binomWOWE$fate)
+
+binomWOWE$fate <- as.numeric(binomWOWE$fate)
+```
+
+### Run stats
+
+```{r}
+wowe <- glm(fate ~ food, data = binomWOWE, family = "binomial")
+
+summary(wowe)
+```
+
+## Binomial of WE outcomes
+
+```{r}
+binomWE <- data %>%
+  select(ID, food, fate)
+
+binomWE$fate <- gsub("wowe mongo", 0, binomWE$fate)
+binomWE$fate <- gsub("wowe", 0, binomWE$fate)
+binomWE$fate <- gsub("em", 1, binomWE$fate)
+binomWE$fate <- gsub("wander", 0, binomWE$fate)
+
+binomWE$fate <- as.numeric(binomWE$fate)
+```
+
+```{r}
+we <- glm(fate ~ food, data = binomWE, family = "binomial")
+
+summary(we)
 ```

### 2022-01-18 MsCcHSFeedOutlineDec15.Rmd
Edited to do correct binomial calculations
Added new wasp survival figure and analyses, relabeled other figure numbers!

@@
 
-# Fig 2: Violin plots of max mass
+# Fig 2: Wasp survival across plant types
+
+```{r}
+datawasp <- data[data$para == "yes", ] %>%
+  select(ID, food, treatment, num.w.coc, num.w.larvae, num.w.eclos)
+
+datawasp <- datawasp[complete.cases(datawasp), ]
+
+datawasp$num.w.tot <- datawasp$num.w.coc + datawasp$num.w.larvae
+datawasp$percent <- (datawasp$num.w.eclos) / (datawasp$num.w.tot)
+```
+
+```{r}
+waspplot <- ggplot(data = datawasp, aes(x = food, y = percent)) +
+  theme_bw() + 
+  geom_boxplot() + 
+  geom_jitter(aes(color = treatment), width = 0.1, height = 0) + 
+  labs(x = "Hostplant", y = "Percent survival from emergence to eclosion", color = "Treatment")
+
+waspplot
+
+ggsave("~/Desktop/waspplot.png", plot = waspplot, width = 8, height = 5)
+
+```
+
+## Statistics
+
+```{r}
+waspbinom <- glm(percent ~ food, family = "binomial", weights = num.w.tot, data = datawasp)
+
+summary(waspbinom)
+
+anova(waspbinom, test = "Chisq")
+
+```
+
+```{r}
+waspbinom2 <- glm(percent ~ food, family = "binomial", weights = num.w.tot, 
+                  data = datawasp[datawasp$treatment == "P NHS", ])
+
+summary(waspbinom2)
+
+anova(waspbinom2, test = "Chisq")
+
+```
+
+```{r}
+waspemerge <- lm(num.w.tot ~ food, data = datawasp)
+
+summary(waspemerge)
+```
+
+```{r}
+waspemergetreat <- lm(num.w.tot ~ treatment, data = datawasp)
+
+summary(waspemergetreat)
+```
+
+# Fig 3: Violin plots of max mass
 
@@
 
-# Fig 3: Developmental outcome proportions
+# Fig 4: Developmental outcome proportions
 
@@
 
-# Fig 4: Maximum mass and age
+# Fig 5: Maximum mass and age
 
@@
 
-# Fig 5: Leaf matter consumed vs. max mass
+# Fig 6: Leaf matter consumed vs. max mass
 
@@
 ```{r}
-binomWOWE <- data %>%
+binomWOWE <- data[data$treatment == "P HS", ] %>%
   select(ID, food, fate)
@@
 ```{r}
-binomWE <- data %>%
+binomWE <- data[data$treatment == "P HS", ] %>%
   select(ID, food, fate)
@@
 summary(we)
+
+anova(we, test = "Chisq")
 ```

### 2022-02-17 MsCcHSFeedOutlineDec15.Rmd
Made a new Fig 2 with Joel's suggestions, saved the other figures to the repo

@@
 ```{r}
+datawasp2 <- datawasp %>%
+  gather(stage, number, num.w.tot, num.w.eclos)
+
+datawasp2$stage <- gsub("num.w.", "", datawasp2$stage)
+datawasp2$stage <- gsub("tot", "Emerged", datawasp2$stage)
+datawasp2$stage <- gsub("eclos", "Eclosed", datawasp2$stage)
+
+datawasp2 <- datawasp2 %>%
+  select(ID, food, treatment, stage, number)
+
+waspmeans <- summarySE(datawasp2, measurevar = "number", groupvars = c("food", "treatment", "stage"))
+waspmeans$stage <- factor(waspmeans$stage, levels = c("Emerged", "Eclosed"))
+waspmeans$comb <- paste(waspmeans$food, waspmeans$treatment, sep = " ")
+```
+
+```{r}
+newwaspplot <- ggplot(data = waspmeans, aes(x = stage, y = number, group = comb, color = treatment)) + 
+  theme_bw() + 
+  geom_line(aes(linetype = food)) + 
+  geom_point(aes(shape = food), size = 3) + 
+  geom_errorbar(aes(ymin = number - se, ymax = number + se), size = 0.25, width = 0.2) + 
+  scale_linetype_manual(values = c("dashed", "solid")) + 
+  scale_shape_manual(values = c(1, 19)) + 
+  labs(x = "Wasp Developmental Stage", y = "Number of wasps per caterpillar host", shape = "Hostplant", 
+       linetype = "Hostplant", color = "Treatment")
+
+newwaspplot
+
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/newwaspplot.png", newwaspplot, width = 8, height = 5)
+```
+
+```{r}
 waspplot <- ggplot(data = datawasp, aes(x = food, y = percent)) +
@@
 
-ggsave("~/Desktop/waspplot.png", plot = waspplot, width = 8, height = 5)
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/waspplot.png", plot = waspplot, width = 8, height = 5)
 
@@
 
-ggsave("~/Desktop/violins2.png", violins, width = 8, height = 5)
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/violins2.png", violins, width = 8, height = 5)
 
@@
 
-ggsave("~/Desktop/outcomesdead.png", plot = barsdead, width = 8, height = 5)
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/outcomesdead.png", plot = barsdead, width = 8, height = 5)
 ```
@@
 
-ggsave("~/Desktop/newmeans.png", newmeans, width = 8, height = 5)
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/newmeans.png", newmeans, width = 8, height = 5)
 ```
@@
 
-ggsave("~/Desktop/newarea.png", newarea, width = 8, height = 5)
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/newarea.png", newarea, width = 8, height = 5)
 ```

### 2022-02-23 MsCcHSFeedOutlineDec15.Rmd
reran wasp emergence stats with ln(#emerged +1)

@@
 datawasp$percent <- (datawasp$num.w.eclos) / (datawasp$num.w.tot)
+datawasp$ln.w.tot <- log(datawasp$num.w.tot + 1)
 ```
@@
 ```{r}
-waspbinom <- glm(percent ~ food, family = "binomial", weights = num.w.tot, data = datawasp)
+waspbinom <- glm(percent ~ food*treatment, family = "binomial", weights = num.w.tot, data = datawasp)
 
@@
 ```{r}
-waspemerge <- lm(num.w.tot ~ food, data = datawasp)
+waspemerge <- lm(ln.w.tot ~ food*treatment, data = datawasp)
 
 summary(waspemerge)
-```
 
-```{r}
-waspemergetreat <- lm(num.w.tot ~ treatment, data = datawasp)
-
-summary(waspemergetreat)
+anova(waspemerge)
 ```

### 2022-02-25 MsCcHSFeedOutlineDec15.Rmd
Made table 1 and deleted extraneous stuff

@@
 library(tidyverse)
-library(Rmisc)
+#library(Rmisc)
 library(lubridate)
@@
 
-```{r}
-waspplot <- ggplot(data = datawasp, aes(x = food, y = percent)) +
-  theme_bw() + 
-  geom_boxplot() + 
-  geom_jitter(aes(color = treatment), width = 0.1, height = 0) + 
-  labs(x = "Hostplant", y = "Percent survival from emergence to eclosion", color = "Treatment")
-
-waspplot
-
-ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/waspplot.png", plot = waspplot, width = 8, height = 5)
-
-```
-
 ## Statistics
@@
 ```{r}
-waspbinom2 <- glm(percent ~ food, family = "binomial", weights = num.w.tot, 
-                  data = datawasp[datawasp$treatment == "P NHS", ])
-
-summary(waspbinom2)
-
-anova(waspbinom2, test = "Chisq")
-
-```
-
-```{r}
 waspemerge <- lm(ln.w.tot ~ food*treatment, data = datawasp)
@@
 anova(waspemerge)
+```
+
+# Table 1: Mean percent eclosion success
+
+```{r}
+eclosmeans <- datawasp %>%
+  group_by(food, treatment) %>%
+    summarise(mean = mean(percent))
+
+eclosmeans
 ```

### 2022-02-25 MsCcHSFeedOutlineDec15.Rmd
Fixed means for eclosion to not run into plyr/dplyr error and get SEs

@@
 library(tidyverse)
-#library(Rmisc)
+library(Rmisc)
 library(lubridate)
@@
 
-# Fig 2: Wasp survival across plant types
+# Table 1: Mean percent eclosion success
 
@@
 ```
+
+```{r}
+eclosmeans <- summarySE(datawasp, measurevar = "percent", groupvars = c("food", "treatment"))
+
+eclosmeans
+```
+
+# Fig 2: Wasp survival across plant types
 
@@
 anova(waspemerge)
-```
-
-# Table 1: Mean percent eclosion success
-
-```{r}
-eclosmeans <- datawasp %>%
-  group_by(food, treatment) %>%
-    summarise(mean = mean(percent))
-
-eclosmeans
 ```

### 2022-03-16 MsCcHSFeedOutlineDec15.Rmd
Changed language from "WOWE" and "WOWE mongo" to "Small WOWE" and "Large WOWE" in graphs

@@
   scale_fill_manual(values = c("purple", "#1E88E5", "lime green", "orange", "#D81B60"),
-                    labels = c("Died", "Wander", "WE", "WOWE", "WOWE mongo"))
+                    labels = c("Died", "Wander", "WE", "Small WOWE", "Large WOWE"))
 
@@
   scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
-                     labels = c("Wander", "WE", "WOWE", "WOWE mongo")) + 
+                     labels = c("Wander", "WE", "Small WOWE", "Large WOWE")) + 
   geom_point(aes(x = ttmax, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
@@
   guides(size = FALSE) + 
-  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (g)", 
+  labs(x = "Age at maximum mass (days)", y = "Maximum mass achieved (g)", 
        shape = "Hostplant Consumed", color = "Developmental Outcome")
@@
   scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
-                     labels = c("Wander", "WE", "WOWE", "WOWE mongo")) + 
+                     labels = c("Wander", "WE", "Small WOWE", "Large WOWE")) + 
   ylim(0, 20) + 
@@
   geom_point(aes(x = area, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
-  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
+  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5, width = 0) + 
   geom_errorbarh(data = datameans2, aes(xmin = area - arease, xmax = area + arease), size = .5) + 

### 2022-09-14 MsCcHSFeedOutlineDec15.Rmd
Added multinomial regression and two-tailed z-test

@@
 library(lmerTest)
+library(nnet)
+library(jmv)
 ```
@@
 ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/outcomesdead.png", plot = barsdead, width = 8, height = 5)
+```
+
+## Stats
+
+Multinomial regression from Katherine to report proportions of outcomes in PHS treatment group
+
+```{r}
+datamulti <- data[data$para == "yes" & data$HS == "yes", ]
+datamulti$fate <- factor(datamulti$fate, levels = c("em", "wander", "wowe", "wowe mongo"), labels = c("WE", "Wander", "Small WOWE", "Large WOWE"))
+datamulti$food <- factor(datamulti$food, levels = c("TB", "DC"))
+```
+
+Use the multinom command to run a model
+
+```{r}
+fatemodel <- multinom(fate ~ food, data = datamulti)
+
+summary(fatemodel)
+```
+
+Get p-values:
+
+```{r}
+fatez <- summary(fatemodel)$coefficients/summary(fatemodel)$standard.errors
+#2-tailed z test
+pfate <- (1-pnorm(abs(fatez), 0, 1))*2
+pfate
 ```

### 2022-11-01 MsCcHSFeedOutlineDec15.Rmd
Added sample sizes to figure 3

@@
 ```{r}
-data$treatment <- factor(data$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
+datadead$treatment <- factor(data$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
 datadead$fate <- factor(datadead$fate, levels = c("dead", "wander", "em", "wowe", "wowe mongo"))
+```
+
+## Make dataframe for annotating in the sample sizes
+
+```{r}
+datadeadsum <- summarySE(datadead, 
+                         measurevar = "mass.max", #doesn't matter, just need the Ns, will be NAs anyways
+                         groupvars = c("treatment", "food"))
+
+samplesize <- data.frame(N = datadeadsum$N, 
+                         treatment = datadeadsum$treatment,
+                         food = datadeadsum$food, 
+                         x = c(1, 1, 2, 2, 3, 3, 4, 4), 
+                         y = 1.05,
+                         fate = NA)
 ```
@@
   facet_wrap(~food) + 
+  scale_y_continuous(breaks = c(0, .25, .5, .75, 1), limits = c(0, 1.07)) + 
   labs(x = "Treatment group", y = "Proportion of indiviudals", fill = "Developmental Outcome") + 
   scale_fill_manual(values = c("purple", "#1E88E5", "lime green", "orange", "#D81B60"),
-                    labels = c("Died", "Wander", "WE", "Small WOWE", "Large WOWE"))
+                    labels = c("Died", "Wander", "WE", "Small WOWE", "Large WOWE")) + 
+  geom_text(data = samplesize, aes(x = x, y = y, label = N))
 

### 2022-11-04 MsCcHSFeedOutlineDec15.Rmd
Added hostplant to Fig 3 violin plots

@@
 dataviolin$fate <- factor(dataviolin$fate, levels = c("wander", "em", "wowe"))
+#dataviolin <- dataviolin[dataviolin$food != "", ]
 
@@
   geom_violin(fill = "light grey", color = "light grey") + 
-  geom_jitter(aes(color = fate), width = 0.1, height = 0) + 
+  geom_jitter(aes(color = fate, shape = food), width = 0.1, height = 0) + 
   theme_bw() + 
-  labs(x = "Treatment Group", y  = "Maximum mass achieved (mg)",  color = "Developmental Outcome") + 
+  labs(x = "Treatment Group", y  = "Maximum mass achieved (mg)",  color = "Developmental Outcome", shape = "Hostplant") + 
   scale_color_manual(values = c("#1E88E5", "lime green", "#D81B60"), 
-                     labels = c("Wander", "WE", "WOWE"))
+                     labels = c("Wander", "WE", "WOWE")) + 
+  scale_shape_manual(values = c(1, 19))
 
@@
 
-ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/violins2.png", violins, width = 8, height = 5)
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/violins3.png", violins, width = 8, height = 5)
 

### 2022-11-08 MsCcHSFeedOutlineDec15.Rmd
Fixed Fig 6 axis label

@@
   guides(size = FALSE) + 
-  labs(x = "Hostplant leaf area consumed (m^2)", y = "Maximum mass achieved (g)", 
+  labs(x = expression(paste("Hostplant leaf area consumed ", (m^{2}))), y = "Maximum mass achieved (g)", 
        shape = "Hostplant Consumed", color = "Developmental Outcome")

### 2022-12-05 MsCcHSFeedOutlineDec15.Rmd
Fixed a slight code bug that made a figure wrong

@@
 ```{r}
-datadead$treatment <- factor(data$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
+datadead$treatment <- factor(datadead$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
 datadead$fate <- factor(datadead$fate, levels = c("dead", "wander", "em", "wowe", "wowe mongo"))

### 2023-01-03 CodeForSubmission.Rmd
Created complete script for manuscript submission

--- 2022-12-05 MsCcHSFeedOutlineDec15.Rmd
@@
 ---
-title: "MsCcHSFeed Outline"
+title: "Code for Submission"
 output: html_notebook
@@
 
+Authors: Anna Parker and Joel Kingsolver
+
+This code contains all analyses and figures for the manuscript. It is organized in order of appearance in the manuscript, with the necessary data manipulations happening between steps as required.
+
+Table of Contents: 
+0. Load in data and packages
+1. Initial data manipulation
+2. Figures, tables, and statistics (in order of appearance)
+  a. Figure 1
+  b. Figure 2 and associated stats
+  c. Figure 3 and Table 1 and associated stats
+  d. Figure 4, Figure 5, Table 2, Supplemental Table 2, and associated stats
+
+## 0. Load in data and packages
+
 ```{r}
+library(tidyverse)
 library(ggplot2)
-library(tidyverse)
 library(Rmisc)
@@
 scan <- read.csv("~/Desktop/MsCcHSFeedLeafScanFinal.csv", header = T)
+datadead <- read.csv("~/Desktop/MsCcHSFeedJan1MOD.csv")
 ```
+
+## 1. Initial data manipulation
 
@@
 ```{r}
-datadead <- read.csv("~/Desktop/MsCcHSFeedJan1MOD.csv")
 datadead <- datadead[datadead$fate != "quink" & datadead$fate != "wander*" & datadead$fate != "?", ]
@@
 
-# Fig 1: Counts
+## 2. Figures and statistics
 
-```{r}
-count(datadead[datadead$food == "TB" & datadead$para == "yes" & datadead$HS == "yes", ])
-count(datadead[datadead$food == "TB" & datadead$para == "yes" & datadead$HS == "no", ])
-count(datadead[datadead$food == "TB" & datadead$para == "no" & datadead$HS == "yes", ])
-count(datadead[datadead$food == "TB" & datadead$para == "no" & datadead$HS == "no", ])
-```
-
-```{r}
-count(datadead[datadead$food == "DC" & datadead$para == "yes" & datadead$HS == "yes", ])
-count(datadead[datadead$food == "DC" & datadead$para == "yes" & datadead$HS == "no", ])
-count(datadead[datadead$food == "DC" & datadead$para == "no" & datadead$HS == "yes", ])
-count(datadead[datadead$food == "DC" & datadead$para == "no" & datadead$HS == "no", ])
-```
-
-# Table 1: Mean percent eclosion success
-
-```{r}
-datawasp <- data[data$para == "yes", ] %>%
-  select(ID, food, treatment, num.w.coc, num.w.larvae, num.w.eclos)
-
-datawasp <- datawasp[complete.cases(datawasp), ]
-
-datawasp$num.w.tot <- datawasp$num.w.coc + datawasp$num.w.larvae
-datawasp$percent <- (datawasp$num.w.eclos) / (datawasp$num.w.tot)
-datawasp$ln.w.tot <- log(datawasp$num.w.tot + 1)
-```
-
-```{r}
-eclosmeans <- summarySE(datawasp, measurevar = "percent", groupvars = c("food", "treatment"))
-
-eclosmeans
-```
-
-# Fig 2: Wasp survival across plant types
-
-```{r}
-datawasp2 <- datawasp %>%
-  gather(stage, number, num.w.tot, num.w.eclos)
-
-datawasp2$stage <- gsub("num.w.", "", datawasp2$stage)
-datawasp2$stage <- gsub("tot", "Emerged", datawasp2$stage)
-datawasp2$stage <- gsub("eclos", "Eclosed", datawasp2$stage)
-
-datawasp2 <- datawasp2 %>%
-  select(ID, food, treatment, stage, number)
-
-waspmeans <- summarySE(datawasp2, measurevar = "number", groupvars = c("food", "treatment", "stage"))
-waspmeans$stage <- factor(waspmeans$stage, levels = c("Emerged", "Eclosed"))
-waspmeans$comb <- paste(waspmeans$food, waspmeans$treatment, sep = " ")
-```
-
-```{r}
-newwaspplot <- ggplot(data = waspmeans, aes(x = stage, y = number, group = comb, color = treatment)) + 
-  theme_bw() + 
-  geom_line(aes(linetype = food)) + 
-  geom_point(aes(shape = food), size = 3) + 
-  geom_errorbar(aes(ymin = number - se, ymax = number + se), size = 0.25, width = 0.2) + 
-  scale_linetype_manual(values = c("dashed", "solid")) + 
-  scale_shape_manual(values = c(1, 19)) + 
-  labs(x = "Wasp Developmental Stage", y = "Number of wasps per caterpillar host", shape = "Hostplant", 
-       linetype = "Hostplant", color = "Treatment")
-
-newwaspplot
-
-ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/newwaspplot.png", newwaspplot, width = 8, height = 5)
-```
-
-## Statistics
-
-```{r}
-waspbinom <- glm(percent ~ food*treatment, family = "binomial", weights = num.w.tot, data = datawasp)
-
-summary(waspbinom)
-
-anova(waspbinom, test = "Chisq")
-
-```
-
-```{r}
-waspemerge <- lm(ln.w.tot ~ food*treatment, data = datawasp)
-
-summary(waspemerge)
-
-anova(waspemerge)
-```
-
-# Fig 3: Violin plots of max mass
+### a. Figure 1
 
@@
 dataviolin$fate <- factor(dataviolin$fate, levels = c("wander", "em", "wowe"))
-#dataviolin <- dataviolin[dataviolin$food != "", ]
+```
 
+#### Graph
+
+```{r}
 violins <- ggplot(data = dataviolin, aes(x = treatment, y = mass.max)) + 
@@
 violins
-
-ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/violins3.png", violins, width = 8, height = 5)
-
 ```
 
-# Fig 4: Developmental outcome proportions
+*Brackets and text annotated in Photoshop*
 
-## Make graph of outcomes
+### b. Figure 2 and stats
 
@@
 
-## Make dataframe for annotating in the sample sizes
+**Make dataframe for annotating in the sample sizes**
 
@@
 
-## This time, keep the dead
+#### Graph
 
@@
   labs(x = "Treatment group", y = "Proportion of indiviudals", fill = "Developmental Outcome") + 
-  scale_fill_manual(values = c("purple", "#1E88E5", "lime green", "orange", "#D81B60"),
+  scale_fill_manual(values = c("dead" = "purple", "wander" = "#1E88E5" , "em" = "lime green", 
+                                       "wowe" = "orange", "wowe mongo" =  "#D81B60"),
                     labels = c("Died", "Wander", "WE", "Small WOWE", "Large WOWE")) + 
@@
 barsdead
-
-ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/outcomesdead.png", plot = barsdead, width = 8, height = 5)
 ```
 
-## Stats
+*Note: Could not get the legend to stop labelling in alphabetical order, so I will switch colors in Photoshop :( *
 
-Multinomial regression from Katherine to report proportions of outcomes in PHS treatment group
+#### Stats
+
+Multinomial regression to report proportions of outcomes in PHS treatment group
 
@@
 
-# Fig 5: Maximum mass and age
+### c. Figure 3, Table 1, Stats
 
-## Manipulate the data
+```{r}
+datawasp <- data[data$para == "yes", ] %>%
+  select(ID, food, treatment, num.w.coc, num.w.larvae, num.w.eclos)
+
+datawasp <- datawasp[complete.cases(datawasp), ]
+
+datawasp$num.w.tot <- datawasp$num.w.coc + datawasp$num.w.larvae
+datawasp$percent <- (datawasp$num.w.eclos) / (datawasp$num.w.tot)
+datawasp$ln.w.tot <- log(datawasp$num.w.tot + 1)
+```
+
+#### Table
+
+```{r}
+eclosmeans <- summarySE(datawasp, measurevar = "percent", groupvars = c("food", "treatment"))
+
+eclosmeans
+```
+
+More manipulation to graph...
+
+```{r}
+datawasp2 <- datawasp %>%
+  gather(stage, number, num.w.tot, num.w.eclos)
+
+datawasp2$stage <- gsub("num.w.", "", datawasp2$stage)
+datawasp2$stage <- gsub("tot", "Emerged", datawasp2$stage)
+datawasp2$stage <- gsub("eclos", "Eclosed", datawasp2$stage)
+
+datawasp2 <- datawasp2 %>%
+  select(ID, food, treatment, stage, number)
+
+waspmeans <- summarySE(datawasp2, measurevar = "number", groupvars = c("food", "treatment", "stage"))
+waspmeans$stage <- factor(waspmeans$stage, levels = c("Emerged", "Eclosed"))
+waspmeans$comb <- paste(waspmeans$food, waspmeans$treatment, sep = " ")
+```
+
+#### Graph
+
+```{r}
+newwaspplot <- ggplot(data = waspmeans, aes(x = stage, y = number, group = comb, color = treatment)) + 
+  theme_bw() + 
+  geom_line(aes(linetype = food)) + 
+  geom_point(aes(shape = food), size = 3) + 
+  geom_errorbar(aes(ymin = number - se, ymax = number + se), size = 0.25, width = 0.2) + 
+  scale_linetype_manual(values = c("dashed", "solid")) + 
+  scale_shape_manual(values = c(1, 19)) + 
+  labs(x = "Wasp Developmental Stage", y = "Number of wasps per caterpillar host", shape = "Hostplant", 
+       linetype = "Hostplant", color = "Treatment")
+
+newwaspplot
+```
+
+#### Stats
+
+Eclosion success:
+```{r}
+waspbinom <- glm(percent ~ food*treatment, family = "binomial", weights = num.w.tot, data = datawasp)
+
+#summary(waspbinom)
+
+anova(waspbinom, test = "Chisq")
+
+```
+
+Emergence totals:
+```{r}
+waspemerge <- lm(ln.w.tot ~ food*treatment, data = datawasp)
+
+#summary(waspemerge)
+
+anova(waspemerge)
+```
+
+### d. Figure 4 + 5, Table 2 + Supp Table 2, Stats
+
+#### Data manipulation
 ```{r}
@@
 
+#Convert from mg to g
 data$mass.max <- data$mass.max / 1000
@@
 
+Code to get total leaf area consumed:
+
 ```{r}
-#1
+#0 - make unique ID for each caterpillar and leaf eaten
 scan$comb <- paste(scan$Caterpillar.ID, "_", scan$Leaf.ID)
 
-#0
+#1 - make an output file
 unique <- unique(scan$comb)
@@
 
-#2-4
+#2-4 - loop through and subset by each unique ID (before and after), then subtract to get area
 for (i in 1:length(consumed$unique)){
@@
 
-#5
+#5 - reseparate cat and leaf ID
 consumed <- consumed %>%
@@
 
-#6
+#6 - make a new output file
 ID <- unique(consumed$catID)
@@
 
-#7
+#7 - loop through and subset by cat ID and add all areas together
 for (i in 1:length(consumedsum$ID)){
@@
 
-#8
+#8 - final data wrangling 
 consumedsum$ID <- as.numeric(consumedsum$ID)
@@
 
+#9 - add to dataframe
 data$area <- consumedsum$totalarea
 
+#10 - change to m^2 fromm cm^2
 data$area <- data$area / 10000
@@
 
+Make new dataframes
 ```{r}
@@
 
-### Group them into one dataframe
+Group means together
 
@@
 ```
+
+#### Graph Fig 4
 
@@
 newmeans
-
-ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/newmeans.png", newmeans, width = 8, height = 5)
 ```
 
-## Stats
-
-### Maximum age differences across treatment and outcome
-
-```{r}
-maxage <- lmer(ttmax ~ fate*food + (1|bin), data = data)
-
-anova(maxage)
-```
-
-```{r}
-maxage2 <- lmer(ttmax ~ para*HS*food + (1|bin), data = data)
-
-anova(maxage2)
-```
-
-```{r}
-AIC(maxage, maxage2)
-```
-
-### Maximum mass
-
-```{r}
-maxmass <- lmer(mass.max ~ fate*food + (1|bin), data = data)
-
-anova(maxmass)
-```
-
-```{r}
-maxmass2 <- lmer(mass.max ~ para*HS*food + (1|bin), data = data)
-
-anova(maxmass2)
-```
-
-```{r}
-AIC(maxmass, maxmass2)
-```
-
-# Fig 6: Leaf matter consumed vs. max mass
+#### Graph Fig 5
 
@@
 newarea
-
-ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/newarea.png", newarea, width = 8, height = 5)
 ```
 
-## Stats
+#### Stats
+
+*Each tests developmental outcome vs. treatment, then compares them via AIC*
+
+**Maximum age differences across treatment and outcome**
+
+```{r}
+maxage <- lmer(ttmax ~ fate*food + (1|bin), data = data)
+
+anova(maxage)
+```
+
+```{r}
+maxage2 <- lmer(ttmax ~ para*HS*food + (1|bin), data = data)
+
+anova(maxage2)
+```
+
+```{r}
+AIC(maxage, maxage2)
+```
+
+**Maximum mass**
+
+```{r}
+maxmass <- lmer(mass.max ~ fate*food + (1|bin), data = data)
+
+anova(maxmass)
+```
+
+```{r}
+maxmass2 <- lmer(mass.max ~ para*HS*food + (1|bin), data = data)
+
+anova(maxmass2)
+```
+
+```{r}
+AIC(maxmass, maxmass2)
+```
+
+**Leaf area consumed**
 
@@
 ```
-
-```{r}
-anova(areatrt, areatrt2)
-```
-
-# Additional analyses
-
-## Binomial of deaths between NP and P groups
-
-```{r}
-binomdeath <- datadead %>%
-  select(ID, food, para, survived)
-
-binomdeath$survived <- gsub("yes", 1, binomdeath$survived)
-binomdeath$survived <- gsub("no", 0, binomdeath$survived)
-
-binomdeath$survived <- as.numeric(binomdeath$survived)
-```
-
-### Run stats
-
-```{r}
-death <- glm(survived ~ food*para, data = binomdeath, family = "binomial")
-
-summary(death)
-```
-
-```{r}
-death2 <- glm(survived ~ para, data = binomdeath, family = "binomial")
-
-summary(death2)
-```
-
-## Binomial of WOWE mongo outcomes
-
-```{r}
-binomWOWE <- data[data$treatment == "P HS", ] %>%
-  select(ID, food, fate)
-
-binomWOWE$fate <- gsub("wowe mongo", 1, binomWOWE$fate)
-binomWOWE$fate <- gsub("wowe", 0, binomWOWE$fate)
-binomWOWE$fate <- gsub("em", 0, binomWOWE$fate)
-binomWOWE$fate <- gsub("wander", 0, binomWOWE$fate)
-
-binomWOWE$fate <- as.numeric(binomWOWE$fate)
-```
-
-### Run stats
-
-```{r}
-wowe <- glm(fate ~ food, data = binomWOWE, family = "binomial")
-
-summary(wowe)
-```
-
-## Binomial of WE outcomes
-
-```{r}
-binomWE <- data[data$treatment == "P HS", ] %>%
-  select(ID, food, fate)
-
-binomWE$fate <- gsub("wowe mongo", 0, binomWE$fate)
-binomWE$fate <- gsub("wowe", 0, binomWE$fate)
-binomWE$fate <- gsub("em", 1, binomWE$fate)
-binomWE$fate <- gsub("wander", 0, binomWE$fate)
-
-binomWE$fate <- as.numeric(binomWE$fate)
-```
-
-```{r}
-we <- glm(fate ~ food, data = binomWE, family = "binomial")
-
-summary(we)
-
-anova(we, test = "Chisq")
-```
-
-# Growth trajectories of different treatment groups
-
-## Manipulate the data
-```{r}
-# Internal process of the loop to convert days to dates
-expt_day <- function(start.date, date){
-  date <- mdy(date)
-  start <- mdy(start.date)
-  diff <- yday(date) - yday(start)
-
-  return(diff)
-}
-
-# Code for the loop itself
-loop <- function(start.date, date.list){
-  days <- rep(NA, length(date.list))
-  for (i in 1:(length(days))){
-    days[i] <- expt_day(start.date = start.date, date = date.list[i])
-  }
-  return(days)
-}
-```
-
-```{r}
-data$day.hatch <- loop(start.date = "07/12/2020", date.list = data$date.hatch)
-data$day.3rd <- loop(start.date = "07/12/2020", date.list = data$date.3rd)
-data$day.4th <- loop(start.date = "07/12/2020", date.list = data$date.4th)
-data$day.5th <- loop(start.date = "07/12/2020", date.list = data$date.5th)
-data$day.w <- loop(start.date = "07/12/2020", date.list = data$date.w)
-
-data$day.5th.2 <- loop(start.date = "07/12/2020", date.list = data$date.5th.2)
-data$day.5th.3 <- loop(start.date = "07/12/2020", date.list = data$date.5th.3)
-data$day.6th <- loop(start.date = "07/12/2020", date.list = data$date.6th)
-data$day.6th.2 <- loop(start.date = "07/12/2020", date.list = data$date.6th.2)
-data$day.6th.3 <- loop(start.date = "07/12/2020", date.list = data$date.6th.3)
-data$day.7th <- loop(start.date = "07/12/2020", date.list = data$date.7th)
-data$day.7th.2 <- loop(start.date = "07/12/2020", date.list = data$date.7th.2)
-data$day.7th.3 <- loop(start.date = "07/12/2020", date.list = data$date.7th.3)
-data$day.coc <- loop(start.date = "07/12/2020", date.list = data$date.coc)
-
-data$tthatch <- 0
-data$tt3rd <- data$day.3rd - data$day.hatch
-data$tt4th <- data$day.4th - data$day.hatch
-data$tt5th <- data$day.5th - data$day.hatch
-data$ttw <- data$day.w - data$day.hatch
-
-data$tt5th.2 <- data$day.5th.2 - data$day.hatch
-data$tt5th.3 <- data$day.5th.3 - data$day.hatch
-data$tt6th <- data$day.6th - data$day.hatch
-data$tt6th.2 <- data$day.6th.2 - data$day.hatch
-data$tt6th.3 <- data$day.6th.3 - data$day.hatch
-data$tt7th <- data$day.7th - data$day.hatch
-data$tt7th.2 <- data$day.7th.2 - data$day.hatch
-data$tt7th.3 <- data$day.7th.3 - data$day.hatch
-data$ttcoc <- data$day.coc - data$day.hatch
-
-```
-
-```{r}
-data$ln.hatch <- log(data$mass.hatch)
-data$ln.3rd <- log(data$mass.3rd)
-data$ln.4th <- log(data$mass.4th)
-data$ln.5th <- log(data$mass.5th)
-data$ln.w <- log(data$mass.w)
-
-data$ln.5th.2 <- log(data$mass.5th.2)
-data$ln.5th.3 <- log(data$mass.5th.3)
-data$ln.6th <- log(data$mass.6th)
-data$ln.6th.2 <- log(data$mass.6th.2)
-data$ln.6th.3 <- log(data$mass.6th.3)
-data$ln.7th <- log(data$mass.7th)
-data$ln.7th.2 <- log(data$mass.7th.2)
-data$ln.7th.3 <- log(data$mass.7th.3)
-data$ln.coc <- log(data$mass.remove)
-
-```
-
-```{r}
-dataslim <- data[data$treatment == "NP NHS" | data$treatment == "NP HS", ] %>%
-  select(ID, food, fate, treatment, tthatch, ln.hatch, tt3rd, ln.3rd, tt4th, ln.4th, tt5th, ln.5th, ttw, ln.w)
-
-dataslim2 <- data[data$treatment == "P NHS" | data$treatment == "P HS", ] %>%
-  select(ID, food, fate, treatment, tthatch, ln.hatch, tt3rd, ln.3rd, tt4th, ln.4th, tt5th, ln.5th, tt5th.2, 
-         ln.5th.2, tt5th.3, ln.5th.3, tt6th, ln.6th, tt6th.2, ln.6th.2, tt6th.3, ln.6th.3, tt7th, ln.7th, 
-         tt7th.2, ln.7th.2, tt7th.3, ln.7th.3, ttcoc, ln.coc )
-```
-
-## NP NHS vs NP HS
-
-### More manupulation
-
-```{r}
-masslong <- dataslim %>%
-  gather(instar, mass, ln.hatch, ln.3rd, ln.4th, ln.5th, ln.w)
-masslong$instar <- gsub("ln.", "", masslong$instar)
-
-agelong <- dataslim %>%
-  gather(instar, age, tthatch, tt3rd, tt4th, tt5th, ttw)
-agelong$instar <- gsub("tt", "", agelong$instar)
-
-masslong <- masslong %>% 
-  select(ID, treatment, food, instar, mass)
-agelong <- agelong %>% 
-  select(ID, treatment, food, instar, age)
-
-datalong<-merge(masslong, agelong, by=c("ID", "treatment", "food", "instar"))
-
-datalong$instar <- factor(datalong$instar, levels = c("hatch", "3rd", "4th", "5th", "w"))
-
-datalong$newtreatment <- paste(datalong$treatment, datalong$food)
-datalong$newtreatment <- factor(datalong$newtreatment, levels = c("NP NHS DC", "NP NHS TB", "NP HS DC", "NP HS TB"))
-```
-
-```{r}
-
-#calculate means and variation
-
-#constructing summarySE for age and mass to make mean plot
-
-masssum <- summarySE(datalong, measurevar = "mass",
-                  groupvars = c("newtreatment", "instar"),
-                  na.rm=TRUE)
-masssum
-
-agesum <- summarySE(datalong, measurevar = "age",
-                   groupvars = c("newtreatment", "instar"),
-                   na.rm = TRUE)
-agesum
-
-#combine into one data frame
-
-masssum$age <- agesum[, 4]
-masssum$age.se <- agesum[, 6]
-masssum$age.ci <- agesum[, 7]
-```
-
-### Plot the data (with CIs)
-
-```{r}
-meanplot <- ggplot(masssum, aes(x = age, y = mass, group = newtreatment, color = newtreatment, shape= newtreatment)) + 
-  theme_bw() + 
-  geom_point(size = 4) + 
-  geom_line(aes(linetype = newtreatment), size = 1) + 
-  geom_errorbar(aes(ymin = mass-(ci/2), ymax = mass + (ci/2)),
-                width = .3, size = 1) + 
-  geom_errorbarh(aes(xmin = age - (age.ci/2), xmax = age + (age.ci/2)),
-                 height = .3, size = 1) + 
-  scale_color_manual(values = c("#D81B60","#1E88E5", "#D81B60","#1E88E5" )) +
-  scale_shape_manual(values = c(1, 1, 2, 2)) + 
-  scale_linetype_manual(values = c("dashed", "dashed", "solid", "solid")) + 
-  labs(x = "Total developmental age (days)", y = "Total mass gained (ln)")
-
-ggsave("meanplot.png", plot = meanplot, width = 8, height = 5)
-
-meanplot
-```
-
-## P NHS v P HS
-
-### Data manipulation - log scale
-
-```{r}
-masslong2 <- dataslim2 %>%
-  gather(instar, mass, ln.hatch, ln.3rd, ln.4th, ln.5th, ln.5th.2, ln.5th.3, ln.6th, ln.6th.2, ln.6th.3, ln.7th,
-         ln.7th.2, ln.7th.3, ln.coc)
-masslong2$instar <- gsub("ln.", "", masslong2$instar)
-
-agelong2 <- dataslim2 %>%
-  gather(instar, age, tthatch, tt3rd, tt4th, tt5th, tt5th.2, tt5th.3, tt6th, tt6th.2, tt6th.3, tt7th, tt7th.2,
-         tt7th.3, ttcoc)
-agelong2$instar <- gsub("tt", "", agelong2$instar)
-
-masslong2 <- masslong2 %>% 
-  select(ID, treatment, food, instar, mass)
-agelong2 <- agelong2 %>% 
-  select(ID, treatment, food, instar, age)
-
-datalong2<-merge(masslong2, agelong2, by=c("ID", "treatment", "food", "instar"))
-
-#datalong2$instar <- factor(datalong2$instar, levels = c("hatch", "3rd", "4th", "5th", "w"))
-
-datalong2$newtreatment <- paste(datalong2$treatment, datalong2$food)
-datalong2$newtreatment <- factor(datalong2$newtreatment, levels = c("P NHS DC", "P NHS TB", "P HS DC", "P HS TB"))
-```
-
-### Individual trajectories - log scale
-
-```{r}
-spaghettiplot <- ggplot(datalong2, aes(x = age, y = mass, group = ID, color = newtreatment, 
-                                     shape= newtreatment)) + 
-  theme_bw() + 
-  geom_point() + 
-  geom_line(aes(linetype = newtreatment), size = .8) + 
-  #geom_errorbar(aes(ymin = mass-(ci/2), ymax = mass + (ci/2)),
-               # width = .3, size = 1) + 
-  #geom_errorbarh(aes(xmin = age - (age.ci/2), xmax = age + (age.ci/2)),
-               #  height = .3, size = 1) + 
-  scale_color_manual(values = c("#D81B60","#1E88E5", "#D81B60","#1E88E5" )) +
-  scale_shape_manual(values = c(1, 1, 2, 2)) + 
-  scale_linetype_manual(values = c("solid", "solid", "dashed", "dashed")) + 
-  labs(x = "Total developmental age (days)", y = "Total mass gained (ln)")
-
-spaghettiplot
-
-ggsave("~/Desktop/lnspaghettiplot.png", plot = spaghettiplot, width = 8, height = 5)
-```
-
-### Data manipulation - normal scale
-
-```{r}
-dataslim3 <- data[data$treatment == "P NHS" | data$treatment == "P HS", ] %>%
-  select(ID, food, fate, treatment, tthatch, mass.hatch, tt3rd, mass.3rd, tt4th, mass.4th, tt5th, mass.5th, tt5th.2, 
-         mass.5th.2, tt5th.3, mass.5th.3, tt6th, mass.6th, tt6th.2, mass.6th.2, tt6th.3, mass.6th.3, tt7th, mass.7th, 
-         tt7th.2, mass.7th.2, tt7th.3, mass.7th.3, ttcoc, mass.remove )
-
-dataslim3$mass.coc <- dataslim3$mass.remove
-
-masslong3 <- dataslim3 %>%
-  gather(instar, mass, mass.hatch, mass.3rd, mass.4th, mass.5th, mass.5th.2, mass.5th.3, mass.6th, mass.6th.2,
-         mass.6th.3, mass.7th, mass.7th.2, mass.7th.3, mass.coc)
-masslong3$instar <- gsub("mass.", "", masslong3$instar)
-
-agelong3 <- dataslim3 %>%
-  gather(instar, age, tthatch, tt3rd, tt4th, tt5th, tt5th.2, tt5th.3, tt6th, tt6th.2, tt6th.3, tt7th, tt7th.2,
-         tt7th.3, ttcoc)
-agelong3$instar <- gsub("tt", "", agelong2$instar)
-
-masslong3 <- masslong3 %>% 
-  select(ID, treatment, food, instar, mass)
-agelong3 <- agelong3 %>% 
-  select(ID, treatment, food, instar, age)
-
-datalong3<-merge(masslong3, agelong3, by=c("ID", "treatment", "food", "instar"))
-
-#datalong2$instar <- factor(datalong2$instar, levels = c("hatch", "3rd", "4th", "5th", "w"))
-
-datalong3$newtreatment <- paste(datalong3$treatment, datalong3$food)
-datalong3$newtreatment <- factor(datalong3$newtreatment, levels = c("P NHS DC", "P NHS TB", "P HS DC", "P HS TB"))
-```
-
-### Graphing - normal scale
-
-```{r}
-spaghettiplot2 <- ggplot(datalong3, aes(x = age, y = mass, group = ID, color = newtreatment, 
-                                     shape= newtreatment)) + 
-  theme_bw() + 
-  geom_point() + 
-  ylim(0, 20000) + 
-  geom_line(aes(linetype = newtreatment), size = .8) + 
-  #geom_errorbar(aes(ymin = mass-(ci/2), ymax = mass + (ci/2)),
-               # width = .3, size = 1) + 
-  #geom_errorbarh(aes(xmin = age - (age.ci/2), xmax = age + (age.ci/2)),
-               #  height = .3, size = 1) + 
-  scale_color_manual(values = c("#D81B60","#1E88E5", "#D81B60","#1E88E5" )) +
-  scale_shape_manual(values = c(1, 1, 2, 2)) + 
-  scale_linetype_manual(values = c("solid", "solid", "dashed", "dashed")) + 
-  labs(x = "Total developmental age (days)", y = "Total mass gained (mg)")
-
-spaghettiplot2
-
-ggsave("~/Desktop/spaghettiplot.png", plot = spaghettiplot2, width = 8, height = 5)
-```
-
-# Wasp emergence
-
-We need to make sure the numbers of wasps emerging and eclosing from TB PNHS and DC PNHS caterpillars is the same with this data.
-
-## Manipulate the data
-
-```{r}
-datawasp <- data %>%
-  select(ID, food, treatment, date.coc, mass.remove, wet, num.w.coc, num.w.larvae, num.w.eclos)
-
-datawasp <- datawasp[complete.cases(datawasp$num.w.coc), ]
-```
-
-```{r}
-datawasp$num.w.tot <- datawasp$num.w.coc + datawasp$num.w.larvae
-datawasp$prop.eclos <- datawasp$num.w.eclos / datawasp$num.w.tot
-```
-
-## Start graphing and running stats
-
-```{r}
-ggplot(data = datawasp, aes(x = treatment, y = num.w.tot)) + 
-  theme_bw() + 
-  geom_boxplot()
-```
-
-```{r}
-ggplot(data = datawasp, aes(x = food, y = num.w.tot)) + 
-  theme_bw() + 
-  geom_boxplot() + 
-  labs(x = "Food Type", y = "Total number of wasps emerged")
-```
-
-```{r}
-waspmod1 <- lm(num.w.tot ~ food, data = datawasp[datawasp$treatment == "P NHS", ])
-
-anova(waspmod1)
-```
-
-```{r}
-ggplot(data = datawasp[datawasp$treatment == "P NHS", ], aes(x = food, y = prop.eclos)) + 
-  theme_bw() + 
-  geom_boxplot() + 
-  labs(x = "Food Type", y = "Proportion of emerged wasps successfully eclosed")
-```
-
-```{r}
-waspmod2 <- glm(prop.eclos ~ food, family = "binomial", data = datawasp[datawasp$treatment == "P NHS", ])
-
-summary(waspmod2)
-```
-
-```{r}
-ggplot(data = datawasp, aes(x = mass.remove, y = num.w.tot, color = food)) + 
-  theme_bw() + 
-  geom_point()
-```
-
-# Redone development time plot - means and SDs
-
-```{r}
-data$day.max <- loop(start.date = "07/12/2020", date.list = data$date.max)
-data$ttmax <- data$day.max - data$day.hatch
-```
-
-```{r}
-datalong4 <- data %>%
-  select(ID, food, treatment, mass.max, ttmax)
-
-meantime <- summarySE(datalong4, measurevar = "ttmax", groupvars = c("food", "treatment"), na.rm = TRUE)
-
-meanmass <- summarySE(datalong4, measurevar = "mass.max", groupvars = c("food", "treatment"), na.rm = TRUE)
-
-datameans <- meantime %>%
-  select(food, treatment, ttmax, sd)
-
-datameans$mass.max <- meanmass$mass.max
-datameans$sdmass <- meanmass$sd
-```
-
-```{r}
-meansbytrt <- ggplot(aes(x = ttmax, y = mass.max, color = food, shape = treatment), data = datalong4) +
-  theme_bw() + 
-  xlim(15, 45) + 
-  geom_point(alpha = 0.4) + 
-  scale_shape_manual(values = c(19, 1, 17, 2)) + 
-  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (g)", 
-       shape = "Treatment", color = "Hostplant Consumed") + 
-  geom_point(data = datameans, aes(x = ttmax, y = mass.max, color = food, shape = treatment), size = 4) + 
-  geom_errorbar(data = datameans, aes(ymin = mass.max - sdmass, ymax = mass.max + sdmass), size = .5) + 
-  geom_errorbarh(data = datameans, aes(xmin = ttmax - sd, xmax = ttmax + sd), size = .5) + 
-  guides(size = FALSE)
-
-meansbytrt
-
-ggsave("~/Desktop/meansbytrt.png", plot = meansbytrt, width = 8, height = 5)
-```
-
-## Add points onto developmental outcomes graph
-
-```{r}
-datalong5 <- data %>%
-  select(ID, food, fate, mass.max, ttmax, area)
-
-meantime2 <- summarySE(datalong5, measurevar = "ttmax", groupvars = c("food", "fate"), na.rm = TRUE)
-
-meanmass2 <- summarySE(datalong5, measurevar = "mass.max", groupvars = c("food", "fate"), na.rm = TRUE)
-```
-
-### Group them into one dataframe
-
-```{r}
-datameans2 <- meantime2 %>%
-  select(food, fate, ttmax, se)
-
-datameans2$mass.max <- meanmass2$mass.max
-datameans2$semass <- meanmass2$se
-
-```
-
-## Graphs with means only
-
-### Maximum mass gained and age at that point

### 2023-01-03 ArchivedCode/Fig1Script.Rmd
Moved scripts for submission

---
title: "Figure 1 Script"
output: html_notebook
---

This script makes Fig. 1, the methods figure.

```{r}
library(ggplot2)
```

```{r}
data <- read.csv("~/Desktop/GitHub/MsCcHSFeed/Data/fig1data.csv", header = TRUE)
```

Create df with labels/annotations for each facet

```{r}
fig1labels <- data.frame(
  label = c("")
)
```

Let's graph it!

```{r}
fig1 <- ggplot(data = data, aes(x = day, y = temp, group = HS, color = outcome)) + 
  theme_bw() + 
  facet_wrap(facets = "para", nrow = 2, ncol = 1) + 
  geom_line() + 
  ylim(22, 42) + 
  labs(x = "Day since molt to 3rd instar", y = "Rearing Temperature (C)") + 
  scale_x_continuous(breaks = seq(1, 8, 1), labels = c("0", "1", "2", "10", "11", "12", "25", "26"), limits = c(0.75, 8)) + 
  scale_color_manual(values = c("#1E88E5", "lime green", "#D81B60")) + 
  theme(strip.background = element_blank(), strip.text = element_blank()) +
  theme(legend.position = "none")

fig1
```

I will add annotations in powerpoint because doing so with facet_wrap is a nightmare!

```{r}
ggsave(filename = "~/Desktop/GitHub/MsCcHSFeed/Figs/Fig1Manuscript.png", plot = fig1, width = 8, height = 5)
```

### 2023-01-03 ArchivedCode/MsCcHSFeedOutlineDec15.Rmd
Moved scripts for submission

--- 2022-12-05 MsCcHSFeedOutlineDec15.Rmd
@@
 
-ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/outcomesdead.png", plot = barsdead, width = 8, height = 5)
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/outcomesdead.png", barsdead, width = 8, height = 5)
 ```
+
+*Note: Could not get the legend to stop labelling in alphabetical order, so I will switch colors in Photoshop :( *
 

### 2023-01-03 ArchivedCode/WorkingScript.Rmd
Moved scripts for submission

--- 2020-09-29 WorkingScript.Rmd
@@
 library(lme4)
+library(lubridate)
 ```
@@
 ```{r}
-data <- read.csv("~/Desktop/MsCcHSFeedSep15modfinal.csv")
+data <- read.csv("~/Desktop/MsCcHSFeedNov30modfinal.csv")
 ```
@@
 ggplot(data, aes(x = mass.max, y = area)) + 
+  theme_bw() + 
   geom_point(aes(color = food)) + 
@@
 ggplot(data, aes(x = mass.max, y = area)) + 
-  geom_point(aes(color = fate))
+  theme_bw() + 
+  geom_point(aes(color = fate, shape = food)) + 
+  #scale_color_viridis_d() + 
+  scale_shape_manual(values = c(19,6)) + 
+  labs(x = "Maximum mass achieved (mg)", y = "Leaf surface area consumed (cm2)")
+```
+```{r}
+data <- data[data$fate != "wander*", ]
+
+modfate <- lmer(mass.max ~ fate*food + (1|bin), data = data)
+
+summary(modfate)
+```
+
+```{r}
+ggplot(data, aes(x = mass.max, y = area)) + 
+  theme_bw() + 
+  geom_point(aes(color = treatment)) + 
+  scale_color_viridis_d() + 
+  labs(x = "Maximum mass achieved (mg)", y = "Leaf surface area consumed (cm2)", color = "Treatment")
 ```
@@
 ```{r}
+mod1.9 <- lm(area ~ food*para*HS, data = data)
+
+summary(mod1.9)
+```
+
+```{r}
 mod2 <- lm(mass.max ~ food*para*HS, data = data)
@@
 summary(mod3)
+```
+
+```{r}
+mod3.5 <- lm(mass.max ~ area, data = data )
+
+summary(mod3.5)
 ```
@@
 ```
+
+## Age vs. Mass plots
+
+```{r}
+# Internal process of the loop to convert days to dates
+expt_day <- function(start.date, date){
+  date <- mdy(date)
+  start <- mdy(start.date)
+  diff <- yday(date) - yday(start)
+
+  return(diff)
+}
+
+# Code for the loop itself
+loop <- function(start.date, date.list){
+  days <- rep(NA, length(date.list))
+  for (i in 1:(length(days))){
+    days[i] <- expt_day(start.date = start.date, date = date.list[i])
+  }
+  return(days)
+}
+
+# Convert all the dates to days
+
+data$day.hatch <- loop(start.date = "07/12/2020", date.list = data$date.hatch)
+data$day.3rd <- loop(start.date = "07/12/2020", date.list = data$date.3rd)
+data$day.4th <- loop(start.date = "07/12/2020", date.list = data$date.4th)
+data$day.5th <- loop(start.date = "07/12/2020", date.list = data$date.5th)
+data$day.w <- loop(start.date = "07/12/2020", date.list = data$date.w)
+data$day.remove <- loop(start.date = "07/12/2020", date.list = data$date.remove)
+#data$day.5th.2 <- loop(start.date = "07/12/2020", date.list = data$date.5th.2)
+#data$day.5th.3 <- loop(start.date = "07/12/2020", date.list = data$date.5th.3)
+#data$day.5th.4 <- loop(start.date = "07/12/2020", date.list = data$date.5th.4)
+#data$day.6th <- loop(start.date = "07/12/2020", date.list = data$date.6th)
+#data$day.6th.2 <- loop(start.date = "07/12/2020", date.list = data$date.6th.2)
+#data$day.6th.3 <- loop(start.date = "07/12/2020", date.list = data$date.6th.3)
+#data$day.7th <- loop(start.date = "07/12/2020", date.list = data$date.7th)
+#data$day.7th.2 <- loop(start.date = "07/12/2020", date.list = data$date.7th.2)
+#data$day.7th.3 <- loop(start.date = "07/12/2020", date.list = data$date.7th.3)
+data$day.max <- loop(start.date = "07/12/2020", date.list = data$date.max)
+```
+
+```{r}
+# Time til each instar
+data$tth <- 0
+data$tt3 <- data$day.3rd - data$day.hatch
+data$tt4 <- data$day.4th - data$day.hatch
+data$tt5 <- data$day.5th - data$day.hatch
+data$ttw <- data$day.w - data$day.hatch
+data$ttrem <- data$day.remove - data$day.hatch
+data$ttmax <- data$day.max - data$day.hatch
+
+# Mass at each instar -> natural log of mass
+
+data$lnh <- log(data$mass.hatch)
+data$ln3 <- log(data$mass.3rd)
+data$ln4 <- log(data$mass.4th)
+data$ln5 <- log(data$mass.5th)
+data$lnw <- log(data$mass.w)
+data$lnrem <- log(data$mass.remove)
+data$lnmax <- log(data$mass.max)
+
+```
+
+```{r}
+masslong <- data %>% gather(instar, mass, mass.3rd, mass.4th, mass.5th, mass.max)
+masslong$instar <- gsub("mass.", "", masslong$instar)
+masslong$instar <- gsub("rd", "", masslong$instar)
+masslong$instar <- gsub("th", "", masslong$instar)
+
+agelong <- data %>% gather(instar, age, tth, tt3, tt4, tt5, ttmax)
+agelong$instar <- gsub("tt", "", agelong$instar)
+
+masslong <- masslong %>% select(ID, treatment, food, instar, mass)
+agelong <- agelong %>% select(ID, treatment, food, instar, age)
+
+datalong <- merge(masslong, agelong, by = c("ID", "treatment", "food", "instar"))
+
+```
+
+```{r}
+lnmasslong <- data %>% gather(instar, mass, lnh, ln3, ln4, ln5, lnw, lnrem, lnmax)
+lnmasslong$instar <- gsub("ln", "", lnmasslong$instar)
+
+lnmasslong <- lnmasslong %>% select(ID, treatment, instar, mass)
+
+lndatalong <- merge(lnmasslong, agelong, by=c("ID", "treatment", "instar"))
+```
+
+```{r}
+devplot <- ggplot(datalong, aes(x = age, y = mass, group = ID, color = treatment, shape = food)) + 
+  theme_bw() + 
+  geom_point() +
+  scale_shape_manual(values = c(1, 19)) + 
+  geom_line(aes(linetype = food), alpha = 0.5) + 
+  scale_linetype_manual(values = c("dotdash", "solid")) + 
+  scale_color_viridis_d() + 
+  labs(x = "Developmental age (days)", y = "Mass gained (mg)", shape = "Hostplant", linetype = "Hostplant", 
+       color = "Treatment group")
+
+devplot
+```
+
+```{r}
+lndevplot <- ggplot(lndatalong, aes(x = age, y = mass, group = ID, color = treatment)) + 
+  geom_point() +
+  geom_line(alpha = 0.5) + 
+  scale_color_viridis_d() + 
+  labs(x = "Developmental age (days)", y = "Natural log of mass gained")
+
+lndevplot
+
+```

### 2023-01-03 CodeForSubmission.Rmd
Changed pathnames in Code

@@
 ```{r}
-data <- read.csv("~/Desktop/MsCcHSFeedJan1MOD.csv")
-scan <- read.csv("~/Desktop/MsCcHSFeedLeafScanFinal.csv", header = T)
-datadead <- read.csv("~/Desktop/MsCcHSFeedJan1MOD.csv")
+data <- read.csv("~/Desktop/GitHub/MsCcHSFeed/Data/MsCcHSFeedJan1MOD.csv")
+scan <- read.csv("~/Desktop/GitHub/MsCcHSFeed/Data/MsCcHSFeedLeafScanFinal.csv", header = T)
+datadead <- read.csv("~/Desktop/GitHub/MsCcHSFeed/Data/MsCcHSFeedJan1MOD.csv")
 ```

### 2023-06-07 CodeForSubmission.Rmd
Removed author info from code.
Addedd faceted Fig. 4 option

@@
 ---
-
-Authors: Anna Parker and Joel Kingsolver
 
@@
 datalong5 <- data %>%
-  select(ID, food, fate, mass.max, ttmax, area)
+  select(ID, food, treatment, fate, mass.max, ttmax, area)
 
@@
 newmeans
+```
+
+```{r}
+datalong5$treatment <- factor(datalong5$treatment, labels = c("Nonparasitized baseline", "Nonparasitized heat shocked", "Parasitized baseline", "Parasitized heat shocked"))
+
+newmeansfacet <- ggplot(data = datalong5, aes(x = ttmax, y = mass.max, color = fate, shape = food)) + 
+  facet_wrap(~ treatment) + 
+  theme_bw() + 
+  xlim(15, 45) +
+  ylim(0, 20) + 
+  geom_point(alpha = 0.8) + 
+  scale_shape_manual(values = c(1, 19)) + 
+  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
+                     labels = c("Wander", "WE", "Small WOWE", "Large WOWE")) + 
+#  geom_point(aes(x = ttmax, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
+#  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
+#  geom_errorbarh(data = datameans2, aes(xmin = ttmax - se, xmax = ttmax + se), size = .5) + 
+#  guides(size = FALSE) + 
+  labs(x = "Age at maximum mass (days)", y = "Maximum mass achieved (g)", 
+       shape = "Hostplant Consumed", color = "Developmental Outcome")
+
+newmeansfacet
 ```

### 2023-06-12 CodeForSubmission.Rmd
Changed all labels on graphs to new terminology, etc.

--- 2023-01-03 CodeForSubmission.Rmd
@@
 library(jmv)
+library(scales)
 ```
@@
 dataviolin <- data
-dataviolin$fate <- gsub(" mongo", "", dataviolin$fate)
-dataviolin$fate <- factor(dataviolin$fate, levels = c("wander", "em", "wowe"))
+#dataviolin$fate <- gsub(" mongo", "", dataviolin$fate)
+#dataviolin$fate <- factor(dataviolin$fate, levels = c("wander", "em", "wowe"))
 ```
@@
 ```{r}
-violins <- ggplot(data = dataviolin, aes(x = treatment, y = mass.max)) + 
+violins <- ggplot(data = dataviolin, aes(x = treatment, y = mass.max/1000)) + 
   geom_violin(fill = "light grey", color = "light grey") + 
@@
   theme_bw() + 
-  labs(x = "Treatment Group", y  = "Maximum mass achieved (mg)",  color = "Developmental Outcome", shape = "Hostplant") + 
-  scale_color_manual(values = c("#1E88E5", "lime green", "#D81B60"), 
-                     labels = c("Wander", "WE", "WOWE")) + 
-  scale_shape_manual(values = c(1, 19))
+  labs(x = "Treatment Group", y  = "Maximum mass achieved (g)",  color = "System Outcome", shape = "Hostplant") + 
+  scale_color_manual(values = c("wander" = "#1E88E5" , "em" = "lime green", 
+                                       "wowe" = "orange", "wowe mongo" =  "#D81B60"),
+                    labels = c("Caterpillar pre-pupation", "Wasp emergence", 
+                               "Wasp larval death", "Wasp egg death")) +
+  scale_shape_manual(values = c(1, 19), labels = c("Devil's claw", "Tobacco"))
 
@@
   scale_y_continuous(breaks = c(0, .25, .5, .75, 1), limits = c(0, 1.07)) + 
-  labs(x = "Treatment group", y = "Proportion of indiviudals", fill = "Developmental Outcome") + 
+  labs(x = "Treatment group", y = "Proportion of indiviudals", fill = "System Outcome") + 
   scale_fill_manual(values = c("dead" = "purple", "wander" = "#1E88E5" , "em" = "lime green", 
                                        "wowe" = "orange", "wowe mongo" =  "#D81B60"),
-                    labels = c("Died", "Wander", "WE", "Small WOWE", "Large WOWE")) + 
+                    labels = c("Died before expt. end", "Caterpillar pre-pupation", "Wasp emergence", 
+                               "Wasp larval death", "Wasp egg death")) + 
   geom_text(data = samplesize, aes(x = x, y = y, label = N))
@@
   geom_errorbar(aes(ymin = number - se, ymax = number + se), size = 0.25, width = 0.2) + 
-  scale_linetype_manual(values = c("dashed", "solid")) + 
-  scale_shape_manual(values = c(1, 19)) + 
+  scale_linetype_manual(values = c("dashed", "solid"), labels = c("Devil's claw", "Tobacco")) + 
+  scale_shape_manual(values = c(1, 19), labels = c("Devil's claw", "Tobacco")) + 
+  scale_color_manual(values = c( "#00BFC4", "#F8766D"), 
+                     labels = c("Parasitized non-heat shocked", "Parasitized heat shocked")) + 
   labs(x = "Wasp Developmental Stage", y = "Number of wasps per caterpillar host", shape = "Hostplant", 
@@
 
+```{r}
+datalong5$treatment <- factor(datalong5$treatment, labels = c("Non-parasitized non-heat shocked", "Non-parasitized heat shocked", "Parasitized non-heat shocked", "Parasitized heat shocked"))
+
+newmeansfacet <- ggplot(data = datalong5, aes(x = ttmax, y = mass.max, color = fate, shape = food)) + 
+  facet_wrap(~ treatment) + 
+  theme_bw() + 
+  xlim(15, 45) +
+  ylim(0, 20) + 
+  geom_point(alpha = 0.8) + 
+  scale_shape_manual(values = c(1, 19), labels = c("Devil's claw", "Tobacco")) + 
+  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
+                     labels = c("Caterpillar pre-pupation", "Wasp emergence", "Wasp larval death", 
+                                "Wasp egg death")) + 
+#  geom_point(aes(x = ttmax, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
+#  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
+#  geom_errorbarh(data = datameans2, aes(xmin = ttmax - se, xmax = ttmax + se), size = .5) + 
+#  guides(size = FALSE) + 
+  labs(x = "Age at maximum mass (days)", y = "Maximum mass achieved (g)", 
+       shape = "Hostplant", color = "System Outcome")
+
+newmeansfacet
+```
+
 #### Graph Fig 5
@@
   geom_point(alpha = 0.4) + 
-  scale_shape_manual(values = c(1, 19)) + 
+  scale_shape_manual(values = c(1, 19), labels = c("Devil's claw", "Tobacaco")) + 
   scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
-                     labels = c("Wander", "WE", "Small WOWE", "Large WOWE")) + 
+                     labels = c("Caterpillar pre-pupation", "Wasp emergence", "Wasp larval death", 
+                                "Wasp egg death")) + 
   ylim(0, 20) + 
@@
   labs(x = expression(paste("Hostplant leaf area consumed ", (m^{2}))), y = "Maximum mass achieved (g)", 
-       shape = "Hostplant Consumed", color = "Developmental Outcome")
+       shape = "Hostplant", color = "System Outcome")
 

### 2023-08-08 CodeForSubmission.Rmd
Changes for next round of revisions (in response to reviewer comments and Joel feedback).

@@
 data <- data[complete.cases(data[, 1]), ]
-data$fate <- factor(data$fate, levels = c("wander", "em", "wowe", "wowe mongo"))
+data$fate <- gsub("wowe mongo", "wowe", data$fate)
+data$fate <- factor(data$fate, levels = c("wander", "em", "wowe"))
 
@@
 datadead$treatment <- factor(datadead$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
+datadead$fate <- gsub("wowe mongo", "wowe", datadead$fate)
 ```
@@
 ## 2. Figures and statistics
-
-### a. Figure 1
-
-```{r}
-data$treatment <- factor(data$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
-
-dataviolin <- data
-#dataviolin$fate <- gsub(" mongo", "", dataviolin$fate)
-#dataviolin$fate <- factor(dataviolin$fate, levels = c("wander", "em", "wowe"))
-```
-
-#### Graph
-
-```{r}
-violins <- ggplot(data = dataviolin, aes(x = treatment, y = mass.max/1000)) + 
-  geom_violin(fill = "light grey", color = "light grey") + 
-  geom_jitter(aes(color = fate, shape = food), width = 0.1, height = 0) + 
-  theme_bw() + 
-  labs(x = "Treatment Group", y  = "Maximum mass achieved (g)",  color = "System Outcome", shape = "Hostplant") + 
-  scale_color_manual(values = c("wander" = "#1E88E5" , "em" = "lime green", 
-                                       "wowe" = "orange", "wowe mongo" =  "#D81B60"),
-                    labels = c("Caterpillar pre-pupation", "Wasp emergence", 
-                               "Wasp larval death", "Wasp egg death")) +
-  scale_shape_manual(values = c(1, 19), labels = c("Devil's claw", "Tobacco"))
-
-violins
-```
-
-*Brackets and text annotated in Photoshop*
 
@@
 datadead$treatment <- factor(datadead$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
-datadead$fate <- factor(datadead$fate, levels = c("dead", "wander", "em", "wowe", "wowe mongo"))
+datadead$fate <- factor(datadead$fate, levels = c("dead", "wander", "em", "wowe"))
+datadead$food <- factor(datadead$food, levels = c("DC", "TB"), labels = c("Devil's claw", "Tobacco"))
 ```
@@
   scale_y_continuous(breaks = c(0, .25, .5, .75, 1), limits = c(0, 1.07)) + 
-  labs(x = "Treatment group", y = "Proportion of indiviudals", fill = "System Outcome") + 
+  labs(x = "Treatment group", y = "Proportion of indiviudals", fill = "Developmental Outcome") + 
   scale_fill_manual(values = c("dead" = "purple", "wander" = "#1E88E5" , "em" = "lime green", 
-                                       "wowe" = "orange", "wowe mongo" =  "#D81B60"),
-                    labels = c("Died before expt. end", "Caterpillar pre-pupation", "Wasp emergence", 
-                               "Wasp larval death", "Wasp egg death")) + 
+                                       "wowe" =  "#D81B60"),
+                    labels = c("Died before expt. end", "Wandering", "Wasp emergence", 
+                               "Without wasp emergence")) + 
   geom_text(data = samplesize, aes(x = x, y = y, label = N))
@@
 
+```{r}
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/Fig2new.png", barsdead, width = 8, height = 5)
+```
+
 #### Stats
@@
 datamulti <- data[data$para == "yes" & data$HS == "yes", ]
-datamulti$fate <- factor(datamulti$fate, levels = c("em", "wander", "wowe", "wowe mongo"), labels = c("WE", "Wander", "Small WOWE", "Large WOWE"))
+datamulti$fate <- factor(datamulti$fate, levels = c("em", "wander", "wowe"), labels = c("WE", "Wander", "WOWE"))
 datamulti$food <- factor(datamulti$food, levels = c("TB", "DC"))
@@
 ```{r}
-newmeans <- ggplot(data = datalong5, aes(x = ttmax, y = mass.max, color = fate, shape = food)) + 
-  theme_bw() + 
-  xlim(15, 45) +
-  geom_point(alpha = 0.4) + 
-  scale_shape_manual(values = c(1, 19)) + 
-  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
-                     labels = c("Wander", "WE", "Small WOWE", "Large WOWE")) + 
-  geom_point(aes(x = ttmax, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
-  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
-  geom_errorbarh(data = datameans2, aes(xmin = ttmax - se, xmax = ttmax + se), size = .5) + 
-  guides(size = FALSE) + 
-  labs(x = "Age at maximum mass (days)", y = "Maximum mass achieved (g)", 
-       shape = "Hostplant Consumed", color = "Developmental Outcome")
-
-newmeans
-```
-
-```{r}
-datalong5$treatment <- factor(datalong5$treatment, labels = c("Non-parasitized non-heat shocked", "Non-parasitized heat shocked", "Parasitized non-heat shocked", "Parasitized heat shocked"))
+datalong5$treatment <- factor(datalong5$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"), labels = c("Non-parasitized non-heat shocked", "Non-parasitized heat shocked", "Parasitized non-heat shocked", "Parasitized heat shocked"))
 
@@
   scale_shape_manual(values = c(1, 19), labels = c("Devil's claw", "Tobacco")) + 
-  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
-                     labels = c("Caterpillar pre-pupation", "Wasp emergence", "Wasp larval death", 
-                                "Wasp egg death")) + 
+  scale_color_manual(values = c("#1E88E5", "lime green", "#D81B60"), 
+                     labels = c("Wandering", "Wasp emergence", "Without wasp emergence")) + 
 #  geom_point(aes(x = ttmax, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
@@
   labs(x = "Age at maximum mass (days)", y = "Maximum mass achieved (g)", 
-       shape = "Hostplant", color = "System Outcome")
+       shape = "Hostplant", color = "Developmental Outcome")
 
 newmeansfacet
+```
+
+```{r}
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/Fig4new.png", newmeansfacet, width = 8, height = 5)
 ```
@@
   theme_bw() + 
-  geom_point(alpha = 0.4) + 
+  geom_point(alpha = 0.8, size = 2.5) + 
   scale_shape_manual(values = c(1, 19), labels = c("Devil's claw", "Tobacaco")) + 
-  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60"), 
-                     labels = c("Caterpillar pre-pupation", "Wasp emergence", "Wasp larval death", 
-                                "Wasp egg death")) + 
+  scale_color_manual(values = c("#1E88E5", "lime green", "#D81B60"), 
+                     labels = c("Wandering", "Wasp emergence", "Without wasp emergence")) + 
   ylim(0, 20) + 
   xlim(0, .6) +
-  geom_point(aes(x = area, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
-  geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5, width = 0) + 
-  geom_errorbarh(data = datameans2, aes(xmin = area - arease, xmax = area + arease), size = .5) + 
+ # geom_point(aes(x = area, y = mass.max, color = fate, shape = food), data = datameans2, size = 4) + 
+ # geom_errorbar(data = datameans2, aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5, width = 0) + 
+ # geom_errorbarh(data = datameans2, aes(xmin = area - arease, xmax = area + arease), size = .5) + 
   guides(size = FALSE) + 
   labs(x = expression(paste("Hostplant leaf area consumed ", (m^{2}))), y = "Maximum mass achieved (g)", 
-       shape = "Hostplant", color = "System Outcome")
+       shape = "Hostplant", color = "Developmental Outcome")
 
 newarea
+```
+
+```{r}
+ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/Fig5new.png", newarea, width = 8, height = 5)
 ```

### 2024-01-10 CodeForSubmission.Rmd
Found a typo in Fig 5 legend -- fixed

@@
   geom_point(alpha = 0.8, size = 2.5) + 
-  scale_shape_manual(values = c(1, 19), labels = c("Devil's claw", "Tobacaco")) + 
+  scale_shape_manual(values = c(1, 19), labels = c("Devil's claw", "Tobacco")) + 
   scale_color_manual(values = c("#1E88E5", "lime green", "#D81B60"), 
